---
title: "FOI_serotype specific"
author: "Phuong Huynh Thi"
date: "5 September 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r set wd, echo=FALSE, message=FALSE}
site <- "HC"
dataInput <-"C2D1" # 6 cases: C1D1, C2D1, C3D1, C1F1, C2F1, C3F1

setwd("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Serotype specific")


##Results from different IS and infecting serotype infering models:
if ( dataInput == "C1D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D1.csv")  
}
if ( dataInput == "C2D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D1.csv")  
}
if ( dataInput == "C3D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D1.csv")  
}
if ( dataInput == "C1F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F1.csv")  
}
if ( dataInput == "C2F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F1.csv")  
}
if ( dataInput == "C3F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F1.csv")  
}


data$YEAR <- as.factor(data$YEAR)
data$predictedIS<- ordered(data$predictedIS,levels=c("Secondary","Primary","Neg"))
data$pred.serotype<- as.factor(data$pred.serotype)

## result from lowest AIC model and homotypic responses were assigned the serotype in advance of applying infecting model
# data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2_to_7_June2018/pop data/models/models_modified_titers/Infecting serotype Models/PredictedIS_batch567_pred.serotype_HomoAssigned.csv")

pop<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]#cross out acute and ELISA samples
pop$Site <- substr(pop$sampleID,1,2)

#Agegroup_ 1year
pop$AgeGroup <-factor(as.factor(floor(pop$Age)),labels=c("[1-2)","[2-3)","[3-4)","[4-5)","[5-6)","[6-7)","[7-8)","[8-9)","[9-10)","[10-11)","[11-12)","[12-13)","[13-14)","[14-15)","[15-16)","[16-17)","[17-18)","[18-19)","[19-20)","[20-21)","[21-22)","[22-23)","[23-24)","[24-25)","[25-26)","[26-27)","[27-28)","[28-29)","[29-30)","[30,31)"))# group as  1year 1 group.

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
## Agegroup_ 2 years : 16groups

# pop$AgeGroup <-factor(as.factor(floor(pop$Age/2)+1),labels=c("[1-2)","[2-4)","[4-6)","[6-8)","[8-10)","[10-12)","[12-14)","[14-16)","[16-18)","[18-20)","[20-22)","[22-24)","[24-26)","[26-28)","[28-30)","[30-31)"))

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
##Agegroup_3years : 11 groups

# pop$AgeGroup <- floor(pop$Age/3) + 1
# pop$AgeGroup[which(pop$AgeGroup == 11)] <- 10
# pop$AgeGroup <- factor(
#   pop$AgeGroup,
#   labels = c("[1-3)","[3-6)","[6-9)","[9-12)","[12-15)","[15-18)",
#              "[18-21)","[21-24)","[24-27)","[27-31)"))


```

# Data input 

**For each age:** 

Numbers of samples:

Number of neg samples:

Numbers of samples classified as primary / numbers of samples classified serotype specific:

Number of samples classified as secondary:


```{r data input, echo=FALSE, message=FALSE}

library(dplyr)
library(tidyr)
# spread(x,y): spread rows of col x into collums, then value of col y will fit in as rows.
#rename(new_name=old_name).
if(site=="HC"){
p_year=dplyr::filter(pop,Site=="HC")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)
# p_year$total <- apply(p_year[,3:8],1,sum,na.rm=T)   
}
if(site=="KH"){
 p_year=dplyr::filter(pop,Site=="KH")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)
# p_year$total <- apply(p_year[,3:8],1,sum,na.rm=T)   
}

p_year$total <-rowSums(p_year[,4:9],na.rm = T)

#create function for substr age rather than put age in order, this is useful in case of missing data in a specific age: 
my_substr <- function(s){
  if (nchar(s) == 5){
    t <- substr(s, 4, 4)
  }else{
    if (nchar(s) == 6){
      t <- substr(s, 4, 5)
    }else{
      t <- substr(s, 5, 6)
    }
  }
  return(t)
}

#
p_year$age<- apply(p_year[,1],1,my_substr)

# Assign NA as 0 because stan does not support NA value:

for (idx in 4:9){
  idx.na <- which(is.na(p_year[[idx]]))
  p_year[[idx]][idx.na] <- 0
}


# setnames(p_year, old=c("AgeGroup","1","2","3","4","Neg","Secondary","total"),new=c("AgeGroup","DV1.13","DV2.13","DV3.13","DV4.13","Neg.13","Sec.13","total.13"))


```

This gets the data in the right format for stan.

```{r data format for stan, echo=FALSE,message=FALSE}

b = length(p_year$age)
datapp<- list(a = b,
              datap=c(p_year[1:b, 8],
                      p_year[1:b, 4],
                      p_year[1:b, 5],
                      p_year[1:b, 6],
                      p_year[1:b, 7],
                      p_year[1:b, 9]),
                      veca=as.integer(p_year$age)) # numbers of neg, prim1,prim2,prim3,prim4,and sec respectively. ## Is these numbers need to be in order?

library(rstan)
# stan code has sections in it: functions, data (where you tell it what form the data will be in), 
#parameters where you say what parameters you are estimating,
#Transformed parameters where you transform these parameters to use in the model
#and the model where you specify how the data and model outcomes are linked

```

# Model code

```{r model code, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
FOI_Dengue <- '

//write function so we can sum things as sum is not built into stan


data {

// HCMC infections
int<lower=0> a;// number of age groups

int veca[a]; //vector age constitute of specific age rather than ages in order.

int datap[6,a]; ////for 2013 this will be sixgroups (neg,primary(1,2,3,4),and secondary  for all age groups)

}

parameters {

vector<lower=0, upper=1>[4] lambda;// 4 DENV serotype


}

transformed parameters {
//the probabilities of being neg, primary and secondary at each age group 
////// HCMC
// need to specify what type of data and how these are...

real pneg[a];// the probabilities of neg at each age group and year
real pprimsero1[a] ; // the probabilities of primary infection of each serotype at each age group and year
real pprimsero2[a] ;
real pprimsero3[a] ;
real pprimsero4[a] ;
real psec[a];// the probabilities of each secondary infection at each age group and year

// calculating all these probabilities
for ( ar in 1:a){

pneg[ar]=exp(-sum(lambda)*veca[ar]);// the prob of neg at each age group and year


pprimsero1[ar]=(exp(-(lambda[2]+lambda[3]+lambda[4])*veca[ar]))*(1-exp(-lambda[1]*veca[ar]));
pprimsero2[ar]=(exp(-(lambda[1]+lambda[3]+lambda[4])*veca[ar]))*(1-exp(-lambda[2]*veca[ar]));
pprimsero3[ar]=(exp(-(lambda[1]+lambda[2]+lambda[4])*veca[ar]))*(1-exp(-lambda[3]*veca[ar]));
pprimsero4[ar]=(exp(-(lambda[1]+lambda[2]+lambda[3])*veca[ar]))*(1-exp(-lambda[4]*veca[ar]));

psec[ar]= 1-pneg[ar]-pprimsero1[ar]-pprimsero2[ar]-pprimsero3[ar]-pprimsero4[ar];// the probabilities of each secondary infection at each age group and year

}
}


model {
//vector to put the model results in
vector[6] vp;

//prior on the parameter we are estimating
lambda~ beta(2,5); 

// the estimates of the things we have data for given the proportions above.

for (ar in 1:a){
vp[1]=pneg[ar];
vp[2]=pprimsero1[ar];
vp[3]=pprimsero2[ar];
vp[4]=pprimsero3[ar];
vp[5]=pprimsero4[ar];
vp[6]=psec[ar];
//likelihood thing assume multinomial
datap[1:6, ar]  ~  multinomial(vp) ;
}
}
'

```

**Some explanation**

**Rhat:** < 1.05 : model perform well

**n-eff ratio** = n-eff/(0.5 * iter * chains) < 1

**Iterations:** 1/2 Warmup : noise data=> exclude?!, 1/2 Sampling


```{r result from model, echo=FALSE, message=FALSE,warning=FALSE, include=FALSE}
# you then run using this: From this output we can quickly assess model convergence by looking at the Rhat values for each parameter. When these are at or near 1, the chains have converged. There are many other diagnostics, but this is an important one for Stan.

fit <- stan(model_code=FOI_Dengue, data=datapp, iter=6000,chains=4, cores = parallel::detectCores())# this may be conducted via 2 steps:  stand_model() and sampling().

posterior <- rstan::extract(fit) # specify package rstan rather than tidyr
# str(posterior)
#this summarizes the parameters, gets mean,etc. of parameters and metrics of whether converged or not like Rhat and neff
foisummary <- summary(fit)
# print(foisummary$summary)

# # plot to see whether estimated parameter is convergence or not: traceplot
# plottedRows <- 1 : nrow(posterior$lambda)
# plottedRows <- which(plottedRows %% 6 == 0)
# plot(posterior$lambda[plottedRows, 4],type="l")

```

# Ploting the result of model and actual data

## Plot the posterior distribution



```{r posterior distribution of lambda, echo=FALSE,fig.height=8,fig.width=12}
#plot the posterior distribution of lambda

#create dataframe for violin plot:
p <- data.frame(lambda = as.numeric(),
                DENV = as.character())

for(a in 1:4){
  p_temp <- data.frame(lambda = posterior$lambda[ , a],
                       DENV = paste0('DENV ', a))
  p <- rbind(p, p_temp)
}

# violin plot
ggplot(p, aes(x=DENV,y=lambda)) + geom_violin()+
  ggtitle(paste("FoI_serotype specific",site,dataInput))+
  theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
        axis.title.x = element_blank(),
        axis.text = element_text(face = "bold"))+
    ylim(0,0.05)+
  # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
  # geom_boxplot(width=0.1)+# add median and quartile
  stat_summary(fun.data=mean_sdl, 
                 geom="pointrange", color="red")#Add mean and standard deviation

# ggsave(filename = paste("FoI_ serotype specific",site,dataInput,".png" ),plot=p2)



```

```{r reload saved image into R}
# library(png)
# 
# img = readPNG("/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Serotype specific/FoI_ serotype specific HC C1D1 .png")
# grid::grid.raster(img)
# 
# 
# 
# 
# Combining all plots in one
library(gridExtra)
library(grid)
# lamb<- grid.arrange(p1,p2,p3,p4,nrow=2,ncol=2)
lamb <- grid.arrange(p1,p2,p3,p4,nrow=2,ncol=2,bottom=textGrob("Posterior lambda distribution_serotype specific",gp=gpar(fontsize=20,font=8,col="dark blue")))



# ggsave(filename ="Posterior lambda distribution_serotype specific.png",plot=lamb )

<!-- ``` -->

