---
title: "FOI_constant"
author: "Phuong Huynh Thi"
date: "5 September 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Setting up
```{r set wd, echo=FALSE}
rm(list=ls())
#packages
library(base)
library(dplyr)
library(tidyr)

# Changeable: site:KH or HC?,dataInput?
site <- "KH" # HC, KH, KH&HC|HC&KH
dataInput <-"C3D1" # 6 cases: C1D1, C2D1, C3D1, C1F1, C2F1, C3F1
#C1D2, C2D2, C3D2, C1D3, C2D3, C3D3, C1F2, C2F2, C3F2,C1F3, C2F3, C3F3

setwd("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Constant")

##Results from different IS and infecting serotype infering models:
if ( dataInput == "C1D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D1.csv")  
}
if ( dataInput == "C2D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D1.csv")  
}
if ( dataInput == "C3D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D1.csv")  
}
if ( dataInput == "C1D2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D2.csv")  
}
if ( dataInput == "C2D2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D2.csv")  
}
if ( dataInput == "C3D2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D2.csv")  
}
if ( dataInput == "C1D3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D3.csv")  
}
if ( dataInput == "C2D3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D3.csv")  
}
if ( dataInput == "C3D3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D3.csv")  
}
if ( dataInput == "C1F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F1.csv")  
}
if ( dataInput == "C2F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F1.csv")  
}
if ( dataInput == "C3F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F1.csv")  
}
if ( dataInput == "C1F2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F2.csv")  
}
if ( dataInput == "C2F2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F2.csv")  
}
if ( dataInput == "C3F2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F2.csv")  
}
if ( dataInput == "C1F3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F3.csv")  
}
if ( dataInput == "C2F3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F3.csv")  
}
if ( dataInput == "C3F3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F3.csv")  
}

data$YEAR <- as.factor(data$YEAR)
data$predictedIS<- ordered(data$predictedIS,levels=c("Secondary","Primary","Neg"))
data$pred.serotype<- as.factor(data$pred.serotype)

pop<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]# cross out acute and ELISA samples
pop$Site <- substr(pop$sampleID,1,2)

#Agegroup_ 1year
pop$AgeGroup <-factor(as.factor(floor(pop$Age)),labels=c("[1-2)","[2-3)","[3-4)","[4-5)","[5-6)","[6-7)","[7-8)","[8-9)","[9-10)","[10-11)","[11-12)","[12-13)","[13-14)","[14-15)","[15-16)","[16-17)","[17-18)","[18-19)","[19-20)","[20-21)","[21-22)","[22-23)","[23-24)","[24-25)","[25-26)","[26-27)","[27-28)","[28-29)","[29-30)","[30,31)"))# group as  1year 1 group.

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
## Agegroup_ 2 years : 16groups

# pop$AgeGroup <-factor(as.factor(floor(pop$Age/2)+1),labels=c("[1-2)","[2-4)","[4-6)","[6-8)","[8-10)","[10-12)","[12-14)","[14-16)","[16-18)","[18-20)","[20-22)","[22-24)","[24-26)","[26-28)","[28-30)","[30-31)"))

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
##Agegroup_3years : 11 groups

# pop$AgeGroup <- floor(pop$Age/3) + 1
# pop$AgeGroup[which(pop$AgeGroup == 11)] <- 10
# pop$AgeGroup <- factor(
#   pop$AgeGroup,
#   labels = c("[1-3)","[3-6)","[6-9)","[9-12)","[12-15)","[15-18)",
#              "[18-21)","[21-24)","[24-27)","[27-31)"))


```

# MODEL 
## Input data
**For each age:** 
numbers of samples:
number of neg samples:
numbers of samples classified as primary:
number of samples classified as secondary:

```{r data input, echo=FALSE}

# spread(x,y): spread rows of col x into collums, then value of col y will fit in as rows.

#rename(new_name=old_name).

if (site=="HC"){
   p_year=dplyr::filter(pop,Site=="HC")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(predictedIS)%>%spread(predictedIS,n)}
if(site == "KH"){
    p_year=dplyr::filter(pop,Site=="KH")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(predictedIS)%>%spread(predictedIS,n)}
if(site == "KH&HC"|site == "HC&KH"){
    p_year=dplyr::filter(pop)%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(predictedIS)%>%spread(predictedIS,n)}

# p_year$total <- apply(p_year[,3:8],1,sum,na.rm=T)

p_year$total <- apply(p_year[,4:6],1,sum,na.rm=T)
p_year <- p_year[order(p_year$YEAR),]

#create function for substr age rather than put age in order, this is useful in case of missing data in a specific age: 
my_substr <- function(s){
  if (nchar(s) == 5){
    t <- substr(s, 4, 4)
  }else{
    if (nchar(s) == 6){
      t <- substr(s, 4, 5)
    }else{
      t <- substr(s, 5, 6)
    }
  }
  return(t)
}

#
p_year$age<- apply(p_year[,1],1,my_substr)

# Assign NA as 0 because stan does not support NA value:

for (idx in 4:6){
  idx.na <- which(is.na(p_year[[idx]]))
  p_year[[idx]][idx.na] <- 0
}



# setnames(p_year, old=c("AgeGroup","1","2","3","4","Neg","Secondary","total"),new=c("AgeGroup","DV1.13","DV2.13","DV3.13","DV4.13","Neg.13","Sec.13","total.13"))


```

## Format input data

For each year in the past up to age a:FOI, in the following code this assumed to be equal across serotypes and the same for all years.

This gets the data in the right format for stan.

```{r data format for stan, echo=FALSE}

b = length(p_year$age)

# number of years: HC: 34 yrs, KH: 35 yrs
n_y <- 2017-2013+max(as.integer(p_year[which(p_year$YEAR==2013),]$age))

l_vecj = length(c(rep(1:round(n_y/5), each =  5)))

datapp<- list(a = b,
              datap=c(p_year[1:b,6],
                      p_year[1:b,5],
                      p_year[1:b,4]),
              veca = as.integer(p_year$age)) # vector of age

library(rstan)

# stanc("/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Constant/Dengue_FOI_constant.stan")

FOI_Dengue <-"~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Constant/Dengue_FOI_constant.stan"


```

## Model simulation
Stan does not support NA in data? => Assign NA as 0

**Some explanation**

Rhat: < 1.05: model perform well
n-eff ratio = n-eff/(0.5 * iter * chains) <1
Iterations: 1/2 Warmup : noise data=> exclude?!, 1/2 Sampling

Posterior distribution (likelihood function= model  and prior distribution: e.g: lamda[0,1] ).

```{r result from model, echo=FALSE}
# you then run using this: From this output we can quickly assess model convergence by looking at the Rhat values for each parameter. When these are at or near 1, the chains have converged. There are many other diagnostics, but this is an important one for Stan.

 fit<-stan(file = FOI_Dengue,
          data=datapp, iter=6000,
          chains=4,
          cores = parallel::detectCores()) # this may be conducted via 2 steps:  stand_model() and sampling().

# # save data for later use without running code again
# saveRDS(fit,paste("FOI constant",p_year$Site[1],dataInput,".rds"))
# # save to another reference repository
# saveRDS(fit,paste("~/Desktop/PMA analysis results/FoI/Constant/rds/FOI constant",p_year$Site[1],dataInput,".rds"))

# fit <- readRDS('/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Constant/FOI constant KH C1D1 .rds')
 
posterior<-rstan::extract(fit) # specify package rstan rather tham tidyr
str(posterior)
#this summarizes the parameters, gets mean,etc. of parameters and metrics of whether converged or not like Rhat and neff
foisummary<-summary(fit)
foisummary
tab <- data.frame(foisummary$summary)

# write.csv(tab, paste("FOI constant",p_year$Site[1],dataInput,".csv"))

```

## Posterior distribution of lambda

```{r posterior distribution of lambda, echo=FALSE,fig.height=8,fig.width=12}
#plot the posterior distribution of lambda
#create dataframe for violin plot:
p <- data.frame(lambda = posterior$lambda)
p$year <- rep("FOI")
# violin plot
lamb <- ggplot(p, aes(x=year,y=lambda)) + geom_violin()+
  ggtitle(paste("posterior lambda _ constant",p_year$Site[1],dataInput))+
  coord_cartesian(ylim=c (0.0,0.03))+
  theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
        axis.title.x = element_blank(),
        axis.text = element_text(face = "bold", angle = 0, hjust = 1))+
  # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
  # geom_boxplot(width=0.1)+# add median and quartile
  stat_summary(fun.data=mean_sdl, 
               geom="pointrange", color="red")#Add mean and standard deviation
lamb
# save the figure
# ggsave(filename=paste("FOI_constant",site,dataInput,".png"), plot = lamb)
# ggsave(filename=paste("~/Desktop/PMA analysis results/FoI/Constant/lamda/FOI_constant",site,dataInput,".png"), plot = lamb)

```

# Visualise the model results

## Traceplot of estimating parameter: lambda

```{r assessing model convergence,echo=FALSE, fig.height=8, fig.width=12}

# # fit<- readRDS("/home/phuonght/pCloudDrive/slides_July2019/models/FOI/Constant/results/Fits/FOI constant HC C1D1 .rds")
# posterior<-rstan::extract(fit) # specify package rstan rather tham tidyr
# # plot to see whether estimated parameter is convergence or not: traceplot
# plottedRows <- 1 : nrow(posterior$lambda)
# plottedRows <- which(plottedRows %% 6 == 0)
# 
# stan_trace(fit, pars="lambda", inc_warmup = F)
# stan_plot(fit,pars = c("pneg","psec"),point_est = "median",show_density = FALSE,ci_level = 0.8, outer_level = 0.95,show_outer_line = TRUE, fill_color = "maroon")
# 
# stan_hist(fit,pars = "lambda")
# 
# stan_dens(fit,pars = "lambda",separate_chains = T)
# 
# stan_ac(fit,pars = "lambda", separate_chains = T)
# 
# stan_trace(fit,pars = "lambda")


```

## Negative

```{r  posterior distribution of neg proportion,echo=FALSE, message=FALSE,fig.height=8,fig.width=12, warning=FALSE}

# p_all_year <- data.frame(neg = as.numeric(),
#                          age = as.character(),
#                          year= as.character())
# 
# 
# for(a in 1:length(p_year$age)){
#   p_temp <- data.frame(neg = posterior$pneg[ , a],
#                        age = paste0(p_year$age[a]),
#                        year= paste0(p_year$YEAR[a]))
#   p_all_year <- rbind(p_all_year, p_temp)
# }
# 
# # relable factor level of age in order
# p_all_year$age <- as.numeric(as.character(p_all_year$age))
# p_all_year <- p_all_year[order(p_all_year$age),]
# p_all_year$age <- as.factor(p_all_year$age)
# 
# library(gridExtra)
# library(grid)
# 
# 
# list_year <- unique(p_all_year$year)
# for (idx.year in 1 : length(list_year)){
#   p <- dplyr::filter(p_all_year,year==list_year[idx.year]) # extract data for each year
# 
#   # length of data frame
#   x_max <- length(p$age)
# 
#   # violin plot
#   list.plot <- list()
# 
#   for (i in 1 : 6){# seperate 6 graphs for each year
#     list.plot[[i]] <- ggplot(p[(5*(i-1)*12000 + 1) : min((5*i*12000), x_max),], aes(x=age,y=neg)) +
#       geom_violin()+
#       theme(plot.subtitle = element_text(hjust=0.5),
#             axis.title = element_blank(),
#             axis.text = element_text(face = "bold"))+
#       # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
#       # geom_boxplot(width=0.1)+# add median and quartile
#       stat_summary(fun.data=mean_sdl,
#                    geom="pointrange", color="red")+#Add mean and sta
#       coord_cartesian(ylim=c(0, 1))
#   }
# 
# 
#   grid.arrange(list.plot[[1]],list.plot[[2]],list.plot[[3]],list.plot[[4]],list.plot[[5]], list.plot[[6]], ncol=3,nrow=2, top =textGrob(paste("posterior distribution of neg_ FOI constant",site,p$year[1]),gp=gpar(fontsize=20,col = "blue")))
# 
# }

```

## Primary

```{r  posterior distribution of primary proportion,echo=FALSE, message=FALSE,fig.height=8,fig.width=12, warning=FALSE}

# p_all_year <- data.frame(prim = as.numeric(),
#                          age = as.character(),
#                          year= as.character())
# 
# 
# for(a in 1:b){
#   p_temp <- data.frame(prim = posterior$pprimsero[ , a],
#                        age = paste0(p_year$age[a]),
#                        year= paste0(p_year$YEAR[a]))
#   p_all_year <- rbind(p_all_year, p_temp)
# }
# 
# # relable factor level of age in order
# p_all_year$age <- as.numeric(as.character(p_all_year$age))
# p_all_year <- p_all_year[order(p_all_year$age),]
# p_all_year$age <- as.factor(p_all_year$age)
# 
# library(gridExtra)
# library(grid)
# 
# 
# list_year <- unique(p_all_year$year)
# for (idx.year in 1 : length(list_year)){
#   p <- dplyr::filter(p_all_year,year==list_year[idx.year]) # extract data for each year
# 
#   # length of data frame
#   x_max <- length(p$age)
# 
#   # violin plot
#   list.plot <- list()
# 
#   for (i in 1 : 6){# seperate 6 graphs for each year
#     list.plot[[i]] <- ggplot(p[(5*(i-1)*12000 + 1) : min((5*i*12000), x_max),], aes(x=age,y=prim)) +
#       geom_violin()+
#       theme(plot.subtitle = element_text(hjust=0.5),
#             axis.title = element_blank(),
#             axis.text = element_text(face = "bold"))+
#       # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
#       # geom_boxplot(width=0.1)+# add median and quartile
#       stat_summary(fun.data=mean_sdl,
#                    geom="pointrange", color="red")+#Add mean and sta
#       coord_cartesian(ylim=c(0, 1))
#   }
# 
# 
# 
#   grid.arrange(list.plot[[1]],list.plot[[2]],list.plot[[3]],list.plot[[4]],list.plot[[5]], list.plot[[6]], ncol=3,nrow=2, top =textGrob(paste("posterior distribution of primary_ FOI constant",site,p$year[1]),gp=gpar(fontsize=20,col = "blue")))
# 
# }



```

## Secondary

```{r  posterior distribution of secondary proportion,echo=FALSE, message=FALSE,fig.height=8,fig.width=12, warning=FALSE}

# p_all_year <- data.frame(sec = as.numeric(),
#                          age = as.character(),
#                          year= as.character())
# 
# 
# for(a in 1:b){
#   p_temp <- data.frame(sec = posterior$psec[ , a],
#                        age = paste0(p_year$age[a]),
#                        year= paste0(p_year$YEAR[a]))
#   p_all_year <- rbind(p_all_year, p_temp)
# }
# 
# # relable factor level of age in order
# p_all_year$age <- as.numeric(as.character(p_all_year$age))
# p_all_year <- p_all_year[order(p_all_year$age),]
# p_all_year$age <- as.factor(p_all_year$age)
# 
# library(gridExtra)
# library(grid)
# 
# 
# list_year <- unique(p_all_year$year)
# for (idx.year in 1 : length(list_year)){
#   p <- dplyr::filter(p_all_year,year==list_year[idx.year]) # extract data for each year
# 
#   # length of data frame
#   x_max <- length(p$age)
# 
#   # violin plot
#   list.plot <- list()
# 
#   for (i in 1 : 6){# seperate 6 graphs for each year
#     list.plot[[i]] <- ggplot(p[(5*(i-1)*12000 + 1) : min((5*i*12000), x_max),],   aes(x=age,y=sec)) +
#       geom_violin()+
#       theme(plot.subtitle = element_text(hjust=0.5),
#             axis.title = element_blank(),
#             axis.text = element_text(face = "bold"))+
#       # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
#       # geom_boxplot(width=0.1)+# add median and quartile
#       stat_summary(fun.data=mean_sdl,
#                    geom="pointrange", color="red")+#Add mean and sta
#       coord_cartesian(ylim=c(0, 1))
#   }
# 
# 
# 
#   grid.arrange(list.plot[[1]],list.plot[[2]],list.plot[[3]],list.plot[[4]],list.plot[[5]], list.plot[[6]], ncol=3,nrow=2, top =textGrob(paste("posterior distribution of secondary_ FOI constant",site,p$year[1]),gp=gpar(fontsize=20,col = "blue")))
# 
# }


```

## Estimated proportions within 95% CI

```{r estimated proportion, echo=FALSE, message=FALSE,fig.height=8,fig.width=12}

pest.all<-data.frame(foisummary$summary)
l_pest.all = length(pest.all$mean) # last row of pest.all
d = (l_pest.all -1 - 1)/3 # 3 group: neg,prim,sec

pest.all<- pest.all[-c(1,l_pest.all),] # only 1 lamda
pest.all$IS <- rep(c("Neg_est","Prim_est","Second_est"),c(d,d,d))
pest.all$AgeGroup<- as.integer(rep(p_year$age,3))
pest.all$YEAR<- as.integer(rep(as.character(p_year$YEAR),3))
# pest.all$year<- as.factor(pest.all$year)
# function to get legend from one of the plots => for nicer looking of muliplot
get_legend<-function(myggplot){
    tmp <- ggplot_gtable(ggplot_build(myggplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    return(legend)
}

#plot
list_year<- unique(pest.all$YEAR)
pp <- list()
for (idx.year in (1 : length(list_year)) ){

    pest <- dplyr::filter(pest.all,YEAR==list_year[idx.year])

    pp[[idx.year]] <- ggplot(pest,aes(x=AgeGroup,y=mean, fill=IS,color=IS))+ geom_line()+
              geom_ribbon(aes(ymin=X2.5., ymax = X97.5.),alpha=0.2)+
              ggtitle(paste(pest$YEAR[1]))+
              xlim(1,31)+
              ylim(0,1)+
              # scale_x_continuous(limits = c(1,31))+
              # scale_y_continuous((limits = c(0,1)))+
              theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
                    axis.text = element_text(face = "bold"),
                    axis.title.y = element_blank())

}

legend <- get_legend(pp[[5]])

library(grid)
library(gridExtra)
grid.arrange(pp[[1]]+theme(legend.position = "none"),
             pp[[2]]+theme(legend.position = "none"),
             pp[[3]]+theme(legend.position = "none"),
             pp[[4]]+theme(legend.position = "none"),
             pp[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste(" Estimated DENV proportion in",site, "_FoI constant "),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page

```


## Fitting data
### Loading real data

Regarding fitting data, the number of samples in each age group is quite small, I gathered samples in groups of 5 years old rather than those of 1. Therefore, there are 6 groups in total: **[1-5), [5-10),[10-15), [15-20), [20-25), [25-31)**


```{r actual proportion_5yrs age,echo=FALSE, message=FALSE,fig.height=8,fig.width=12}

# CI95%
library(DescTools)
library(data.table)

pop1<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]# cross out acute and ELISA samples
pop1$Site <- substr(pop1$sampleID,1,2)

##Agegroup_5years : 6 groups

pop1$AgeGroup <- floor(pop1$Age/5) + 1
pop1$AgeGroup[which(pop1$AgeGroup == 7)]<- 6
pop1$AgeGroup <- factor(
  pop1$AgeGroup,
  labels = c("[1-5)","[5-10)","[10-15)","[15-20)","[20-25)","[25-31)"))

p13CI.all=dplyr::filter(pop1,Site==paste(site))%>%group_by(AgeGroup,YEAR)%>%dplyr::count(predictedIS)%>%spread(predictedIS,n)
setnames(p13CI.all, old="Neg", new="Negative")

# Assign NA as 0:

for (idx in 3:5){
  idx.na <- which(is.na(p13CI.all[[idx]]))
  p13CI.all[[idx]][idx.na] <- 0
}

p13CI.all<- tidyr::gather(p13CI.all,"IS","n",3:5)# gather 3 variables (Neg,Prim,Secondary) into 1 variables called "IS"

p13CI.all<- p13CI.all[order(p13CI.all$YEAR,p13CI.all$AgeGroup),]# sort data by year

p13CI.all<- dplyr::mutate(p13CI.all,est=0,lwr.ci=0,upr.ci=0)# create cols for importing result from multinomCI.

for ( i in seq(1,length(p13CI.all$AgeGroup),by=3)){# every 3 rows ,do....
  p13CI.all[i:(i+2),5:7] <- MultinomCI(c(p13CI.all$n[i:(i+2)]))
}

# # plot
# for (idx.year in ( 1 : length(list_year))){
#   p13CI <- dplyr::filter(p13CI.all,YEAR==list_year[idx.year])
#   print(ggplot(p13CI, aes(x=AgeGroup,y=est, fill=IS,color=IS))+ geom_point()+
#           ggtitle(paste("Proportions",site,p13CI$YEAR[1]))+
#           theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5))+
#           geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25, position=position_dodge(0.2)))
# 
# }

```

### Seperated figures

```{r estimated prop vs actual prop ,echo=FALSE,fig.height=8,fig.width=12, eval=FALSE }
# # actual proportion
# p<- p13CI.all
# p<- p[order(p$IS),]
# 
# # #create function for substr assigning age group as one value, this create the same age structure with p1 data frame below. This function has run in previous chunk => no need re-run in this chunk!
# #
# # my_substr <- function(s){
# #   if (nchar(s) == 5){
# #     t <- substr(s, 4, 4)
# #   }else{
# #     if (nchar(s) == 6){
# #       t <- substr(s, 4, 5)
# #     }else{
# #       t <- substr(s, 5, 6)
# #     }
# #   }
# #   return(t)
# # }
# 
# #
# p$AgeGroup<- apply(p[,1],1,my_substr)
# p <- p[,-4]
# 
# # estimated proportion
# p1 <- pest.all[,c("AgeGroup","YEAR","IS","mean","X2.5.","X97.5.")]
# 
# colnames(p1)<- c("AgeGroup","YEAR","IS","est","lwr.ci","upr.ci")
# 
# pc.all<- rbind(data.frame(p), data.frame(p1))
# 
# 
# pc.all$AgeGroup <- as.numeric(pc.all$AgeGroup)
# 
# #plot negatives
# for ( idx.year in (1:length(list_year))){
# 
#   pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
# 
#   print(
#     ggplot(pc%>%filter(IS=="Neg_est"|IS=="Negative"),
#            aes(x=AgeGroup,y=est, fill=IS, color=IS))+
#       geom_point()+
#       xlim (1,31)+
#       ylim (0,1)+
#       ggtitle(paste("Neg_FOI_constant",site,pc$YEAR[1]))+
#       theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
#             axis.text = element_text(face = "bold"))+
#       geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit
#   )
# }
# 
# #plot primary
# for ( idx.year in (1:length(list_year))){
# 
#   pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
# 
#   print(
#     ggplot(pc%>%filter(IS=="Prim_est"|IS=="Primary"),
#            aes(x=AgeGroup,y=est, fill=IS, color=IS))+
#       geom_point()+
#       xlim (1,31)+
#       ylim (0,1)+
#       ggtitle(paste("Prim_FOI_constant",site,pc$YEAR[1]))+
#       theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
#             axis.text = element_text(face = "bold"))+
#       geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit
#   )
# }
# 
# #plot secondary
# for ( idx.year in (1:length(list_year))){
# 
#   pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
# 
#   print(
#     ggplot(pc%>%filter(IS=="Second_est"|IS=="Secondary"),
#            aes(x=AgeGroup,y=est, fill=IS, color=IS))+
#       geom_point()+
#       xlim (1,31)+
#       ylim (0,1)+
#       ggtitle(paste("Sec_FOI_constant",site,pc$YEAR[1]))+
#       theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
#             axis.text = element_text(face = "bold"))+
#       geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit
#   )
# }
# 


```

### all yrs in one plot

```{r estimated prop and actual prop_ all years in one plot,echo=FALSE,fig.height=8,fig.width=12 }
p<- p13CI.all
p<- p[order(p$IS),]

# #create function for substr assigning age group as one value, this create the same age structure with p1 data frame below. This function has run in previous chunk => no need re-run in this chunk!
# 
# my_substr <- function(s){
#   if (nchar(s) == 5){
#     t <- substr(s, 4, 4)
#   }else{
#     if (nchar(s) == 6){
#       t <- substr(s, 4, 5)
#     }else{
#       t <- substr(s, 5, 6)
#     }
#   }
#   return(t)
# }

#
p$AgeGroup<- apply(p[,1],1,my_substr)
p <- p[,-4]

# estimated proportion
p1 <- pest.all[,c("AgeGroup","YEAR","IS","mean","X2.5.","X97.5.")]

colnames(p1)<- c("AgeGroup","YEAR","IS","est","lwr.ci","upr.ci")

pc.all<- rbind(data.frame(p), data.frame(p1))
pc.all$AgeGroup <- as.numeric(pc.all$AgeGroup)

# # function to get legend from one of the plots => for nicer looking of muliplot => runned in chunk 12
# get_legend<-function(myggplot){
#     tmp <- ggplot_gtable(ggplot_build(myggplot))
#     leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
#     legend <- tmp$grobs[[leg]]
#     return(legend)
#     }

#plot negatives

neg <- list() # create empty list for input graphs in for loop
for ( idx.year in (1:length(list_year))){
    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
    
    neg[[idx.year]] <- ggplot(pc%>%filter(IS=="Neg_est"|IS=="Negative"),
                              aes(x=AgeGroup,y=est, fill=IS, color=IS))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+
        
        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit 
    
}

legend <- get_legend(neg[[5]])

library(grid)
library(gridExtra)
negplot<-grid.arrange(neg[[1]]+theme(legend.position = "none"),
             neg[[2]]+theme(legend.position = "none"),
             neg[[3]]+theme(legend.position = "none"),
             neg[[4]]+theme(legend.position = "none"),
             neg[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV negatives in",site, "_FoI constant",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page 

# # save the figure
# ggsave(filename=paste("~/Desktop/PMA analysis results/FoI/Constant/fits/Neg_data fit",site, "_FoI constant",dataInput,".png"),plot=negplot)

#plot primary
prim <- list()
for ( idx.year in (1:length(list_year))){
    
    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
    
    prim[[idx.year]]<- ggplot(pc%>%filter(IS=="Prim_est"|IS=="Primary"),
                              aes(x=AgeGroup,y=est, fill=IS, color=IS))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+
        
        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit 
    
}

legend <- get_legend(prim[[5]])
primplot <- grid.arrange(prim[[1]]+theme(legend.position = "none"),
             prim[[2]]+theme(legend.position = "none"),
             prim[[3]]+theme(legend.position = "none"),
             prim[[4]]+theme(legend.position = "none"),
             prim[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV primary infection in",site, "_FoI constant ",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page 

# # save the figure
# ggsave(filename=paste("~/Desktop/PMA analysis results/FoI/Constant/fits/Prim_data fit",site, "_FoI constant",dataInput,".png"),plot=primplot)

#plot secondary
sec <- list()
for ( idx.year in (1:length(list_year))){
    
    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
    
    
    sec[[idx.year]] <- ggplot(pc%>%filter(IS=="Second_est"|IS=="Secondary"),
                              aes(x=AgeGroup,y=est, fill=IS, color=IS))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+
        
        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit 
    
}

legend <- get_legend(sec[[5]])
secplot <- grid.arrange(sec[[1]]+theme(legend.position = "none"),
             sec[[2]]+theme(legend.position = "none"),
             sec[[3]]+theme(legend.position = "none"),
             sec[[4]]+theme(legend.position = "none"),
             sec[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV secondary infection in",site, "_FoI constant",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page 

# # save the figure
# ggsave(filename=paste("~/Desktop/PMA analysis results/FoI/Constant/fits/Sec_data fit",site, "_FoI constant",dataInput,".png"),plot=secplot)

```

## Combining all lamda from different model for comparison

```{r }
for(i in (1: 6)){
  site_vec <- c("HC","HC","HC","KH","KH","KH")
  data_vec <- c("C1D1", "C2D1", "C3D1","C1D1", "C2D1", "C3D1")
  
  site <- site_vec[i]
  dataInput <-data_vec[i]
  #Loading stored simulation results
  fit <- readRDS(paste("~/Desktop/PMA analysis results/FoI/Constant/rds/FOI constant",site,dataInput,".rds"))# Loading the fit object (no need run over again)
  posterior<-rstan::extract(fit)
  
  p <- data.frame(lambda = posterior$lambda)
  p$year <- rep("FOI")
  
  p[i]<-ggplot(p, aes(x=year,y=lambda)) + geom_violin()+
    ggtitle(paste(site,dataInput))+
    coord_cartesian(ylim=c (0.0,0.03))+
    theme(plot.title = element_text(hjust=0.5,face="bold",size=12,colour = "blue"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.text = element_text(face = "bold", angle = 0, hjust = 1))+
    # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
    # geom_boxplot(width=0.1)+# add median and quartile
    stat_summary(fun.data=mean_sdl,
                 geom="pointrange", color="red")#Add mean and standard deviation
}

library(gridExtra)
library(grid)
lamb<- grid.arrange(p1,p2,p3,p4,p5,p6,nrow=2,ncol=3,bottom=textGrob("Posterior lambda distribution_constant",gp=gpar(fontsize=20,font=8,col="dark blue")))

  # # ggsave(filename ="Posterior lambda distribution_constant.png",plot=lamb )
  # ggsave(filename ="~/Desktop/PMA analysis results/FoI/Constant/lamda/Posterior lambda distribution_constant.png",plot=lamb )


```


