---
title: "FOI_time varying and serotype specific"
author: "Phuong Huynh Thi"
date: "22 July 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Data preparation

```{r Initial setup,}
# Initial setup
############################################################
setwd("/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Time varying _ serotype specific")

rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())

util <- new.env()
source('stan_utility.R', local=util) # this code from Michael Betancourt

```

```{r changeable parameters, echo=FALSE, message=FALSE}
# Changeable
site <- "KH" #KH, HC,HC&KH, KH&HC
dataInput <-"C2F1" # C1D1, C1F1
step_year <- 1 # 1,2,3,4,5

# # for loop for run at once
# site_vec <- c("KH","HC","KH&HC")
# dataInput_vec <- c("C1D1","C1F1")
# step_year_vec <- c(1:5)
# 
# for (idx_site_vec in 1:length(site_vec)){
#     for (idx_dataInput_vec in 1: length(dataInput_vec)){
#         for (idx_step_year_vec in 1: length(step_year_vec)){
#             
#             site <- site_vec[idx_site_vec]
#             dataInput <- dataInput_vec[idx_dataInput_vec]
#             step_year <- step_year_vec[idx_step_year_vec]
#             code function ........
#         }
#     }
# }


#Input:results from different IS and infecting serotype infering models:
if ( dataInput == "C1D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D1.csv")  
}
if ( dataInput == "C2D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D1.csv")  
}
if ( dataInput == "C3D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D1.csv")  
}
if ( dataInput == "C1F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F1.csv")  
}
if ( dataInput == "C2F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F1.csv")  
}
if ( dataInput == "C3F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F1.csv")  
}

data$YEAR <- as.factor(data$YEAR)
data$predictedIS<- ordered(data$predictedIS,levels=c("Secondary","Primary","Neg"))
data$pred.serotype<- as.factor(data$pred.serotype)

# Extract population data only!
pop<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]#cross out acute and ELISA samples
pop$Site <- substr(pop$sampleID,1,2)

# Age grouping

##Agegroup_ 1year
pop$AgeGroup <-factor(as.factor(floor(pop$Age)),labels=c("[1-2)","[2-3)","[3-4)","[4-5)","[5-6)","[6-7)","[7-8)","[8-9)","[9-10)","[10-11)","[11-12)","[12-13)","[13-14)","[14-15)","[15-16)","[16-17)","[17-18)","[18-19)","[19-20)","[20-21)","[21-22)","[22-23)","[23-24)","[24-25)","[25-26)","[26-27)","[27-28)","[28-29)","[29-30)","[30,31)"))# group as  1year 1 group.

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
## Agegroup_ 2 years : 16groups

# pop$AgeGroup <-factor(as.factor(floor(pop$Age/2)+1),labels=c("[1-2)","[2-4)","[4-6)","[6-8)","[8-10)","[10-12)","[12-14)","[14-16)","[16-18)","[18-20)","[20-22)","[22-24)","[24-26)","[26-28)","[28-30)","[30-31)"))

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
##Agegroup_3years : 11 groups

# pop$AgeGroup <- floor(pop$Age/3) + 1
# pop$AgeGroup[which(pop$AgeGroup == 11)] <- 10
# pop$AgeGroup <- factor(
#   pop$AgeGroup,
#   labels = c("[1-3)","[3-6)","[6-9)","[9-12)","[12-15)","[15-18)",
#              "[18-21)","[21-24)","[24-27)","[27-31)"))
#              
             
```


```{r data input, echo=FALSE, message=FALSE}

library(dplyr)
library(tidyr)
# spread(x,y): spread rows of col x into collums, then value of col y will fit in as rows.
#rename(new_name=old_name).

if (site=="HC"){
    p_year=dplyr::filter(pop,Site=="HC")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)}
if(site == "KH"){
    p_year=dplyr::filter(pop,Site=="KH")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)}
if(site == "KH&HC"|site =="HC&KH"){
    p_year=dplyr::filter(pop)%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)}


# p_year$total <- apply(p_year[,3:8],1,sum,na.rm=T)
p_year$total <-rowSums(p_year[,4:9],na.rm = T)

#create function for substr age rather than put age in order, this is useful in case of missing data in a specific age: 
my_substr <- function(s){
  if (nchar(s) == 5){
    t <- substr(s, 4, 4)
  }else{
    if (nchar(s) == 6){
      t <- substr(s, 4, 5)
    }else{
      t <- substr(s, 5, 6)
    }
  }
  return(t)
}

#
p_year$age<- apply(p_year[,1],1,my_substr)

# Assign NA as 0 because stan does not support NA value:

for (idx in 4:9){
  idx.na <- which(is.na(p_year[[idx]]))
  p_year[[idx]][idx.na] <- 0
}

# setnames(p_year, old=c("AgeGroup","1","2","3","4","Neg","Secondary","total"),new=c("AgeGroup","DV1.13","DV2.13","DV3.13","DV4.13","Neg.13","Sec.13","total.13"))


```

This gets the data in the right format for stan.

```{r data format for stan, echo=FALSE,message=FALSE}

b = length(p_year$age)
n_y = 2017-2013+1+max(as.integer(p_year[which(p_year$YEAR==2013),]$age)) # number of years backward, time period that data is available ## KH: 36 -> 1982, HC: 35 -> 1983

if ( step_year == 2){
    if ( site == "KH"|site =="KH&HC"|site =="HC&KH"){
        vecj = as.integer(c(rep(1:floor(n_y/2), each =  2))) # for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/2), each =  2),17)) # for HC 
    }
} else if (step_year == 3){
    if ( site == "KH"|site =="KH&HC"|site =="HC&KH"){
        vecj = as.integer(c(rep(1:floor(n_y/3), each =  3))) #for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/3), each =  3),11,11)) # for HC ##11th year 2 yrs as a group 
    }
}else if (step_year == 4){
    if ( site == "KH"|site =="KH&HC"|site =="HC&KH"){
        vecj = as.integer(c(rep(1:floor(n_y/4), each =  4))) #for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/4), each =  4),9,9,9)) # for HC 
    }
}else if (step_year == 5){
    if ( site == "KH"|site =="KH&HC"|site =="HC&KH"){
        vecj = as.integer(c(rep(1:floor(n_y/5), each =  5),7)) #for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/5), each =  5))) # for HC 
    }
}else { # step_year = 1
    vecj = as.integer(1:n_y)
}

lamb_y = length(unique(vecj)) # number of lambda by time


datapp<- list(a = b,
              datap=c(p_year[1:b, 8],
                      p_year[1:b, 4],
                      p_year[1:b, 5],
                      p_year[1:b, 6],
                      p_year[1:b, 7],
                      p_year[1:b, 9]),
              vecj = vecj,
              lamb_y = lamb_y,
              veca = as.integer(p_year$age), # age
              vecy = as.integer(as.character(p_year$YEAR)),# year
              n_y = n_y)


# numbers of neg,prim1,prim2,prim3,prim4,and sec respectively. 

library(rstan)
# stan code has sections in it: functions, data (where you tell it what form the data will be in), 
#parameters where you say what parameters you are estimating,
#Transformed parameters where you transform these parameters to use in the model
#and the model where you specify how the data and model outcomes are linked

```


# Model code : save in *.stan format 


```{r check wrote model, }


## First, we should check our Stan model to make sure we wrote a syntactically correct file 

# stanc("/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2_to_7_June2018/pop data/models/FOI/time varying _ serotype specific/Stan codes/annual FoI_group less info yrs.stan")


## Now let’s save that file path.

# stan_model <- "/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Time varying _ serotype specific/Stan codes/annual FoI_group less info yrs.stan"

stan_model <- "/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Time varying _ serotype specific/Stan codes/FOI_time varying_serotype specific.stan"



```

**Posterior Predictive Checks**

For prediction and as another form of model diagnostic, Stan can use random number generators to generate predicted values for each data point, at each iteration. This way we can generate predictions that also represent the uncertainties in our model and our data generation process. We generate these using the **Generated Quantities block**. This block can be used to get any other information we want about the posterior, or **make predictions for new data**.
Note that vectorization is not supported in the GQ (generated quantities) block, so we have to put it in a loop. But since this is compiled to C++, loops are actually quite fast and Stan only evaluates the GQ block once per iteration, so it won’t add too much time to your sampling. Typically, the data generating functions will be the distributions you used in the model block but with an **_rng suffix**. (Double-check in the Stan manual to see which sampling statements have corresponding rng functions already coded up.)

*Convergence Diagnostics*

Before we go on, we should check again the Rhat values, the effective sample size (n_eff), and the traceplots of our model parameters to make sure the model has converged and is reliable.

**Some explanation**

**Rhat:** < 1.05 : model perform well

**n-eff ratio** = n-eff/(0.5 * iter * chains) < 1

**Iterations:** 1/2 Warmup : noise data=> exclude?!, 1/2 Sampling


```{r model fitting, echo=FALSE, message=FALSE,warning=FALSE, include=FALSE}

fit <- stan(file = stan_model, data=datapp, iter=6000,chains=4, cores = parallel::detectCores()) # this may be conducted via 2 steps:  stand_model() and sampling().

##save data for later use without running code again
saveRDS(fit,paste("FOI timevarying_serotypes",step_year,"yr(s)",site,dataInput,".rds"))

# # plot prior distribution
# p = seq(0,1, length=100)
# plot(p, dbeta(p, 2, 5), ylab="density", type ="l", col=4)
# plot(p, dbeta(p, 2, 9 ), ylab="density", type ="l", col=4)

# Check diagnostics
util$check_all_diagnostics(fit)

posterior <- rstan::extract(fit) # specify package rstan rather than tidyr
# str(posterior)
foisummary<-summary(fit)
foisummary
tab <- data.frame(foisummary$summary)
write.csv(tab, paste("FOI timevarying_serotypes",step_year,"yr(s)",site,dataInput,".csv"))

```


```{r visualize lambda distibution, echo=FALSE,fig.height=8,fig.width=12}

# setwd("/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2_to_7_June2018/pop data/models/FOI")

#create dataframe for violin plot:
    
p <- data.frame(lambda = as.numeric(),
                DENV = as.character())

for(a in 1:4){
  p_temp <- data.frame(lambda = posterior$lambda[,a,],
                       DENV = paste0('DENV ', a))
  p <- rbind(p, p_temp)
}

## Grouping less info. yrs >>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
# #1. renames colnames of dataframe p as year, group less info. yrs
# if ( site == "HC"){
#     if ( step_year == 1)
#     {names(p) <- c(2017:1988,"87-83","DENV")}
#     if ( step_year ==2){
#         names(p) <- c("2017-2016","2015-2014","2013-2012","2011-2010","2009-2008","2007-2006","2005-2004","2003-2002","2001-2000","1999-1998","1997-1996","1995-1994","1993-1992","1991-1990","1989-1988","1987-1986","1985-1983","DENV")}
#     if (step_year ==5){
#         names(p) <- c("2017-2013","2012-2008","2007-2003","2002-1998","1997-1993","1992-1988","1987-1983","DENV")
#     }
# }else if ( site == "KH"){
# 
#     if ( step_year == 1)
#     {names(p) <- c(2017:1988,"87-82","DENV")}
#     if ( step_year ==2){
#         names(p) <- c("2017-2016","2015-2014","2013-2012","2011-2010","2009-2008","2007-2006","2005-2004","2003-2002","2001-2000","1999-1998","1997-1996","1995-1994","1993-1992","1991-1990","1989-1988","1987-1986","1985-1982","DENV")}
#     if (step_year ==5){
#         names(p) <- c("2017-2013","2012-2008","2007-2003","2002-1998","1997-1993","1992-1988","1987-1982","DENV")
# 
#     }}
# 
# #2. for step_year==1 and grouping less info. yrs
# if (site == "HC"){ # for HC
#     DV1 <- p[1:12000,-(n_y-4+1)]
#     DV2 <- p[(12001:24000),-(n_y-4+1)]
#     DV3 <- p[24001:36000,-(n_y-4+1)]
#     DV4 <- p[36001:48000,-(n_y-4+1)]
# }else if (site == "KH"){ # for KH
#     DV1 <- p[1:12000,-(n_y-5+1)]
#     DV2 <- p[(12001:24000),-(n_y-5+1)]
#     DV3 <- p[24001:36000,-(n_y-5+1)]
#     DV4 <- p[36001:48000,-(n_y-5+1)]
# }

# Not grouping the very last years
#1.renames colnames of dataframe p as year, not grouping less info.yrs
if ( site == "HC"){
    if ( step_year == 1)# 35 lambda
    {names(p) <- c(2017:1983,"DENV")}
    if ( step_year ==2){# 17 lambda
        names(p) <- c("2017-2016","2015-2014","2013-2012","2011-2010","2009-2008","2007-2006","2005-2004","2003-2002","2001-2000","1999-1998","1997-1996","1995-1994","1993-1992","1991-1990","1989-1988","1987-1986","1985-1983","DENV")}
    if ( step_year ==3){# 11 lambda
        names(p) <- c("2017-2015","2014-2012","2011-2009","2008-2006","2005-2003","2002-2000","1999-1997","1996-1994","1993-1991","1990-1988","1987-1983","DENV")}
    if ( step_year ==4){# 9 lambda
        names(p) <- c("2017-2014","2013-2010","2009-2006","2005-2002","2001-1998","1997-1994","1993-1990","1989-1986","1985-1983","DENV")}
    if (step_year ==5){ #7 lambda
        names(p) <- c("2017-2013","2012-2008","2007-2003","2002-1998","1997-1993","1992-1988","1987-1983","DENV")
    }
}else if ( site == "KH"|site =="KH&HC"|site =="HC&KH"){

    if ( step_year == 1) # 36 lambda
    {names(p) <- c(2017:1982,"DENV")}
    if ( step_year ==2){# 18 lambda
        names(p) <- c("2017-2016","2015-2014","2013-2012","2011-2010","2009-2008","2007-2006","2005-2004","2003-2002","2001-2000","1999-1998","1997-1996","1995-1994","1993-1992","1991-1990","1989-1988","1987-1986","1985-1984","1983-1982","DENV")}
     if ( step_year ==3){# 12 lambda
        names(p) <- c("2017-2015","2014-2012","2011-2009","2008-2006","2005-2003","2002-2000","1999-1997","1996-1994","1993-1991","1990-1988","1987-1985","1984-1982","DENV")}
    if ( step_year ==4){# 9 lambda
        names(p) <- c("2017-2014","2013-2010","2009-2006","2005-2002","2001-1998","1997-1994","1993-1990","1989-1986","1985-1982","DENV")}
    if (step_year ==5){ # 7 lambda
        names(p) <- c("2017-2013","2012-2008","2007-2003","2002-1998","1997-1993","1992-1988","1987-1982","DENV")

    }}


#2. violin plot, not grouping less info. yrs
    DV1 <- p[1:12000,-(lamb_y+1)]
    DV2 <- p[(12001:24000),-(lamb_y+1)]
    DV3 <- p[24001:36000,-(lamb_y+1)]
    DV4 <- p[36001:48000,-(lamb_y+1)]




# tranform data frame for ploting

library(data.table)
DV1 <- melt(DV1,id.vars=0) # transformed data frame
DV2 <- melt(DV2,id.vars=0)
DV3 <- melt(DV3,id.vars=0)
DV4 <- melt(DV4,id.vars=0)

# DV1
p1 <- ggplot(DV1,aes(x=variable,y=value)) +
      geom_violin()+
      # geom_boxplot(width=0.1)+
        # ggtitle(paste("posterior lambda _ age varying_serotype specific",p_year$Site[1]))+
        theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
              axis.title.x = element_blank(),
              # axis.text.x = element_text(angle = 90, hjust = 0.5,
              axis.text.x = element_blank())+
        coord_cartesian(ylim=c(-0.01,0.3))+
        ylab("DENV1")+
        # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
        # geom_boxplot(width=0.1)+# add median and quartile
        stat_summary(fun.data=mean_sdl, 
                     geom="pointrange", color="red")#Add mean and standard deviation
#DV2   
p2 <- ggplot(DV2,aes(x=variable,y=value)) + 
      geom_violin()+
      # geom_boxplot(width=0.1)+
        # ggtitle(paste("posterior lambda _ age varying_serotype specific",p_year$Site[1]))+
        theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
              axis.title.x = element_blank(),
              # axis.text.x = element_text(angle = 90, hjust = 0.5,
              axis.text.x = element_blank())+
        coord_cartesian(ylim=c(-0.01,0.3))+
        ylab("DENV2")+
        # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
        # geom_boxplot(width=0.1)+# add median and quartile
        stat_summary(fun.data=mean_sdl, 
                     geom="pointrange", color="red")#Add mean and standard deviation
    
#DV3
p3 <- ggplot(DV3,aes(x=variable,y=value)) + 
      geom_violin()+
      # geom_boxplot(width=0.1)+
        # ggtitle(paste("posterior lambda _ age varying_serotype specific",p_year$Site[1]))+
        theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
              axis.title.x = element_blank(),
              axis.text.x = element_text(angle = 90,,size=6,face = "bold"))+
              # axis.text.x = element_blank())+
        coord_cartesian(ylim=c(-0.01,0.3))+
        ylab("DENV3")+
        # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
        # geom_boxplot(width=0.1)+# add median and quartile
        stat_summary(fun.data=mean_sdl, 
                     geom="pointrange", color="red")#Add mean and standard deviation
    
#DV4
p4 <- ggplot(DV4,aes(x=variable,y=value)) +
      geom_violin()+
      # geom_boxplot(width=0.1)+
        # ggtitle(paste("posterior lambda _ age varying_serotype specific",p_year$Site[1]))+
        theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
              axis.title.x = element_blank(),
              axis.text.x = element_text(angle = 90, ,size=6,face = "bold"))+
        coord_cartesian(ylim=c(-0.01,0.3))+
        ylab("DENV4")+
        # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
        # geom_boxplot(width=0.1)+# add median and quartile
        stat_summary(fun.data=mean_sdl, 
                     geom="pointrange", color="red")#Add mean and standard deviation
    

library(gridExtra)
library(grid)


lamb <- grid.arrange(p1,p2,p3,p4, ncol=2,nrow=2, top =textGrob(paste("FOI_time varying",step_year,"yr(s)","_serotype specific",site,dataInput),gp=gpar(fontsize=20,col = "blue")))

# save the figure
ggsave(filename=paste("FOI timevarying_serotype",step_year,"yr(s)",site,dataInput,".png"), plot = lamb)


```
