---
title: "FOI_serotype specific"
author: "Phuong Huynh Thi"
date: "5 September 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Initial set up
```{r set wd, echo=FALSE, message=FALSE}
rm(list = ls())

library(base)
library(dplyr)
library(tidyr)

site <- "KH"
dataInput <-"C3F3" # 6 cases: C1D1, C2D1, C3D1, C1F1, C2F1, C3F1
#C1D2, C2D2, C3D2, C1D3, C2D3, C3D3, C1F2, C2F2, C3F2,C1F3, C2F3, C3F3

setwd("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Serotype specific")


##Results from different IS and infecting serotype infering models:
if ( dataInput == "C1D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D1.csv")  
}
if ( dataInput == "C2D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D1.csv")  
}
if ( dataInput == "C3D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D1.csv")  
}
if ( dataInput == "C1D2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D2.csv")  
}
if ( dataInput == "C2D2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D2.csv")  
}
if ( dataInput == "C3D2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D2.csv")  
}
if ( dataInput == "C1D3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D3.csv")  
}
if ( dataInput == "C2D3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D3.csv")  
}
if ( dataInput == "C3D3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D3.csv")  
}
if ( dataInput == "C1F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F1.csv")  
}
if ( dataInput == "C2F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F1.csv")  
}
if ( dataInput == "C3F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F1.csv")  
}
if ( dataInput == "C1F2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F2.csv")  
}
if ( dataInput == "C2F2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F2.csv")  
}
if ( dataInput == "C3F2"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F2.csv")  
}
if ( dataInput == "C1F3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F3.csv")  
}
if ( dataInput == "C2F3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F3.csv")  
}
if ( dataInput == "C3F3"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F3.csv")  
}


data$YEAR <- as.factor(data$YEAR)
data$predictedIS<- ordered(data$predictedIS,levels=c("Secondary","Primary","Neg"))
data$pred.serotype<- as.factor(data$pred.serotype)

## result from lowest AIC model and homotypic responses were assigned the serotype in advance of applying infecting model
# data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2_to_7_June2018/pop data/models/models_modified_titers/Infecting serotype Models/PredictedIS_batch567_pred.serotype_HomoAssigned.csv")

pop<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]#cross out acute and ELISA samples
pop$Site <- substr(pop$sampleID,1,2)

#Agegroup_ 1year
pop$AgeGroup <-factor(as.factor(floor(pop$Age)),labels=c("[1-2)","[2-3)","[3-4)","[4-5)","[5-6)","[6-7)","[7-8)","[8-9)","[9-10)","[10-11)","[11-12)","[12-13)","[13-14)","[14-15)","[15-16)","[16-17)","[17-18)","[18-19)","[19-20)","[20-21)","[21-22)","[22-23)","[23-24)","[24-25)","[25-26)","[26-27)","[27-28)","[28-29)","[29-30)","[30,31)"))# group as  1year 1 group.

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
## Agegroup_ 2 years : 16groups

# pop$AgeGroup <-factor(as.factor(floor(pop$Age/2)+1),labels=c("[1-2)","[2-4)","[4-6)","[6-8)","[8-10)","[10-12)","[12-14)","[14-16)","[16-18)","[18-20)","[20-22)","[22-24)","[24-26)","[26-28)","[28-30)","[30-31)"))

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
##Agegroup_3years : 11 groups

# pop$AgeGroup <- floor(pop$Age/3) + 1
# pop$AgeGroup[which(pop$AgeGroup == 11)] <- 10
# pop$AgeGroup <- factor(
#   pop$AgeGroup,
#   labels = c("[1-3)","[3-6)","[6-9)","[9-12)","[12-15)","[15-18)",
#              "[18-21)","[21-24)","[24-27)","[27-31)"))


```

# Data input 

**For each age:** 

Numbers of samples:

Number of neg samples:

Numbers of samples classified as primary / numbers of samples classified serotype specific:

Number of samples classified as secondary:


```{r data input, echo=FALSE, message=FALSE}

# spread(x,y): spread rows of col x into collums, then value of col y will fit in as rows.
#rename(new_name=old_name).
if(site=="HC"){
p_year=dplyr::filter(pop,Site=="HC")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)
# p_year$total <- apply(p_year[,3:8],1,sum,na.rm=T)   
}
if(site=="KH"){
 p_year=dplyr::filter(pop,Site=="KH")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)
# p_year$total <- apply(p_year[,3:8],1,sum,na.rm=T)   
}

p_year$total <-rowSums(p_year[,4:9],na.rm = T)

#create function for substr age rather than put age in order, this is useful in case of missing data in a specific age: 
my_substr <- function(s){
  if (nchar(s) == 5){
    t <- substr(s, 4, 4)
  }else{
    if (nchar(s) == 6){
      t <- substr(s, 4, 5)
    }else{
      t <- substr(s, 5, 6)
    }
  }
  return(t)
}

#
p_year$age<- apply(p_year[,1],1,my_substr)

# Assign NA as 0 because stan does not support NA value:

for (idx in 4:9){
  idx.na <- which(is.na(p_year[[idx]]))
  p_year[[idx]][idx.na] <- 0
}


# setnames(p_year, old=c("AgeGroup","1","2","3","4","Neg","Secondary","total"),new=c("AgeGroup","DV1.13","DV2.13","DV3.13","DV4.13","Neg.13","Sec.13","total.13"))


```

This gets the data in the right format for stan.

```{r data format for stan, echo=FALSE,message=FALSE}

b = length(p_year$age)
datapp<- list(a = b,
              datap=c(p_year[1:b, 8],
                      p_year[1:b, 4],
                      p_year[1:b, 5],
                      p_year[1:b, 6],
                      p_year[1:b, 7],
                      p_year[1:b, 9]),
                      veca=as.integer(p_year$age)) # numbers of neg, prim1,prim2,prim3,prim4,and sec respectively. ## Is these numbers need to be in order?

library(rstan)
# stan code has sections in it: functions, data (where you tell it what form the data will be in), 
#parameters where you say what parameters you are estimating,
#Transformed parameters where you transform these parameters to use in the model
#and the model where you specify how the data and model outcomes are linked

```

# Model code

```{r model code, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
FOI_Dengue <- '

//write function so we can sum things as sum is not built into stan


data {

// HCMC infections
int<lower=0> a;// number of age groups

int veca[a]; //vector age constitute of specific age rather than ages in order.

int datap[6,a]; ////for 2013 this will be sixgroups (neg,primary(1,2,3,4),and secondary  for all age groups)

}

parameters {

vector<lower=0, upper=1>[4] lambda;// 4 DENV serotype


}

transformed parameters {
//the probabilities of being neg, primary and secondary at each age group 
////// HCMC
// need to specify what type of data and how these are...

real pneg[a];// the probabilities of neg at each age group and year
real pprimsero1[a] ; // the probabilities of primary infection of each serotype at each age group and year
real pprimsero2[a] ;
real pprimsero3[a] ;
real pprimsero4[a] ;
real psec[a];// the probabilities of each secondary infection at each age group and year

// calculating all these probabilities
for ( ar in 1:a){

pneg[ar]=exp(-sum(lambda)*veca[ar]);// the prob of neg at each age group and year


pprimsero1[ar]=(exp(-(lambda[2]+lambda[3]+lambda[4])*veca[ar]))*(1-exp(-lambda[1]*veca[ar]));
pprimsero2[ar]=(exp(-(lambda[1]+lambda[3]+lambda[4])*veca[ar]))*(1-exp(-lambda[2]*veca[ar]));
pprimsero3[ar]=(exp(-(lambda[1]+lambda[2]+lambda[4])*veca[ar]))*(1-exp(-lambda[3]*veca[ar]));
pprimsero4[ar]=(exp(-(lambda[1]+lambda[2]+lambda[3])*veca[ar]))*(1-exp(-lambda[4]*veca[ar]));

psec[ar]= 1-pneg[ar]-pprimsero1[ar]-pprimsero2[ar]-pprimsero3[ar]-pprimsero4[ar];// the probabilities of each secondary infection at each age group and year

}
}


model {
//vector to put the model results in
vector[6] vp;

//prior on the parameter we are estimating
lambda~ beta(2,5); 

// the estimates of the things we have data for given the proportions above.

for (ar in 1:a){
vp[1]=pneg[ar];
vp[2]=pprimsero1[ar];
vp[3]=pprimsero2[ar];
vp[4]=pprimsero3[ar];
vp[5]=pprimsero4[ar];
vp[6]=psec[ar];
//likelihood thing assume multinomial
datap[1:6, ar]  ~  multinomial(vp) ;
}
}
'
# FOI_Dengue <-"/home/phuong/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Serotype specific/FOI_serotype_specific.stan"

```

#Model simulation
**Some explanation**

**Rhat:** < 1.05 : model perform well

**n-eff ratio** = n-eff/(0.5 * iter * chains) < 1

**Iterations:** 1/2 Warmup : noise data=> exclude?!, 1/2 Sampling


```{r result from model, echo=FALSE, message=FALSE,warning=FALSE, include=FALSE}
# you then run using this: From this output we can quickly assess model convergence by looking at the Rhat values for each parameter. When these are at or near 1, the chains have converged. There are many other diagnostics, but this is an important one for Stan.

fit <- stan(model_code=FOI_Dengue, data=datapp, iter=6000,chains=4, cores = parallel::detectCores())# this may be conducted via 2 steps:  stand_model() and sampling().

# # save data for later use without running code again
# saveRDS(fit,paste("FOI serotype specific",p_year$Site[1],dataInput,".rds"))
saveRDS(fit,paste("~/Desktop/PMA analysis results/FoI/serotype specific/rds/FOI serotype specific",p_year$Site[1],dataInput,".rds"))

# fit <- readRDS('/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Constant/FOI constant KH C1D1 .rds')

posterior <- rstan::extract(fit) # specify package rstan rather than tidyr
# str(posterior)
#this summarizes the parameters, gets mean,etc. of parameters and metrics of whether converged or not like Rhat and neff
foisummary <- summary(fit)
# print(foisummary$summary)

# # plot to see whether estimated parameter is convergence or not: traceplot
# plottedRows <- 1 : nrow(posterior$lambda)
# plottedRows <- which(plottedRows %% 6 == 0)
# plot(posterior$lambda[plottedRows, 4],type="l")

```

# Visualize the results
## lambda distribution

```{r posterior distribution of lambda, echo=FALSE,fig.height=8,fig.width=12}
#plot the posterior distribution of lambda

#create dataframe for violin plot:
p <- data.frame(lambda = as.numeric(),
                DENV = as.character())

for(a in 1:4){
  p_temp <- data.frame(lambda = posterior$lambda[ , a],
                       DENV = paste0('DENV ', a))
  p <- rbind(p, p_temp)
}

# violin plot
lamb = ggplot(p, aes(x=DENV,y=lambda)) + geom_violin()+
  ggtitle(paste("FoI_serotype specific",site,dataInput))+
  theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
        axis.title.x = element_blank(),
        axis.text = element_text(face = "bold"))+
    ylim(0,0.05)+
  # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
  # geom_boxplot(width=0.1)+# add median and quartile
  stat_summary(fun.data=mean_sdl, 
                 geom="pointrange", color="red")#Add mean and standard deviation
lamb

ggsave(filename = paste("FoI_ serotype specific",site,dataInput,".png" ),plot=lamb)

```

When Stan goes wrong?
· "Divergent transitions after warmup"
· Means Stan is taking steps that are too big.
· Can fix by manually increasing the desired average acceptance probably,
adapt_delta, above it's default of 0.8
chain1 <‐ stan(file="bayes_LASSO.stan",data=data,iter=50000, chains=1,
cores=1,control = list(**adapt_delta = 0.99**,
max_treedepth = 15))
· This will slow your chain down but may result in a better sample
## Trace plots

```{r trace plot visualize,echo=FALSE, fig.height=8, fig.width=12}

# # Changeable: site:KH or HC?, step year 1, 2 or 5
# site <- "HC"
# dataInput <-"C1D1" # 6 cases: C1D1, C2D1, C3D1, C1F1, C2F1, C3F1
# step_year <- 1 # 1 to 5
# # reload object fit if it is not current running
# fit <- readRDS("/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Time varying/FOI_time varying.rds ")


# # plot to see whether estimated parameter is convergence or not: traceplot
# # plottedRows <- 1 : nrow(posterior$lambda)
# # plottedRows <- which(plottedRows %% 6 == 0)
# # plot(posterior$lambda[plottedRows, 7],type="l")
# 
# stan_trace(fit,pars=c("lambda[1]", 'lambda[2]'))
# stan_trace(fit,pars= "lambda")
# 
# stan_trace(fit,pars="pneg[1]")
# # We can also look at the posterior densities & histograms.
# 
# stan_dens(fit,pars=c("lambda[1]", 'lambda[2]'))
# stan_hist(fit, pars = c("psec[1]"))
# stan_plot(fit)
# 
# # And we can generate plots which indicate the mean parameter estimates and any credible intervals we may be interested in. Depending on the variance in your own data, when you do your own analyses, you might see smaller or larger credible intervals.
# 
# stan_plot(fit,pars="lambda", show_density = F, ci_level = 0.5, outer_level = 0.95, fill_color = "salmon")
# 
# 
# stan_plot(fit,pars = c("pneg","psec"),point_est = "median",show_density = FALSE,ci_level = 0.8, outer_level = 0.95,show_outer_line = TRUE, fill_color = "maroon")
# 
# stan_scat(fit,pars = c("pneg","psec"))
# 
# 
# stan_ac(fit,pars = "lambda", separate_chains = T)
# 
# pairs(fit, pars="lambda")
# 
# sampler_params <- get_sampler_params(fit)


```


## Estimated proportions within 95% CI


```{r estimated proportion, echo=FALSE, message=FALSE,fig.height=8,fig.width=12}

pest.all<-data.frame(foisummary$summary)
l_pest.all = length(pest.all$mean) # last row of pest.all
d = (l_pest.all - 4- 1)/6 # 6 groups: neg,prim(1,3,3,4),sec

pest.all<- pest.all[-c(1:4,l_pest.all),] # exlude  number of lamda( 4 lambda), and last row
pest.all$Serostatus <- rep(c("Neg_est","Prim1_est","Prim2_est","Prim3_est","Prim4_est","Second_est"),c(d,d,d,d,d,d))
pest.all$AgeGroup<- as.integer(rep(p_year$age,6))
pest.all$YEAR<- as.integer(rep(as.character(p_year$YEAR),6))
# pest.all$year<- as.factor(pest.all$year)

# function to get legend from one of the plots => for nicer looking of muliplot 
get_legend<-function(myggplot){
    tmp <- ggplot_gtable(ggplot_build(myggplot))
    leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
    legend <- tmp$grobs[[leg]]
    return(legend)
}

#plot

list_year<- unique(pest.all$YEAR)

pp <- list()
for (idx.year in (1 : length(list_year)) ){
    
    pest <- dplyr::filter(pest.all,YEAR==list_year[idx.year])
    
    pp[[idx.year]] <- ggplot(pest,aes(x=AgeGroup,y=mean, fill=Serostatus,color=Serostatus))+ geom_line()+
              geom_ribbon(aes(ymin=X2.5., ymax = X97.5.),alpha=0.2)+
              ggtitle(paste(pest$YEAR[1]))+
              xlim(1,31)+
              ylim(0,1)+
              # scale_x_continuous(limits = c(1,31))+
              # scale_y_continuous((limits = c(0,1)))+
              theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
                    axis.text = element_text(face = "bold"),
                    axis.title.y = element_blank())
    
}

legend <- get_legend(pp[[5]])

library(grid)
library(gridExtra)
grid.arrange(pp[[1]]+theme(legend.position = "none"),
             pp[[2]]+theme(legend.position = "none"),
             pp[[3]]+theme(legend.position = "none"),
             pp[[4]]+theme(legend.position = "none"),
             pp[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste(" Estimated DENV proportion in", site,dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page 


```


# MODEL FITTING

Regarding actual data, the number of samples in each age group is quite small, I gathered samples in groups of 5 years old rather than those of 1. Therefore, there are 6 groups in total: **[1-5), [5-10),[10-15), [15-20), [20-25), [25-30)**

## pop data

```{r actual proportion_5yrs age,echo=FALSE, message=FALSE,fig.height=8,fig.width=12}
# CI95%
library(DescTools)
library(data.table)

pop1<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]# cross out acute and ELISA samples
pop1$Site <- substr(pop1$sampleID,1,2)

##Agegroup_5years : 6 groups

pop1$AgeGroup <- floor(pop1$Age/5) + 1
pop1$AgeGroup[which(pop1$AgeGroup == 7)]<- 6
pop1$AgeGroup <- factor(
  pop1$AgeGroup,
  labels = c("[1-5)","[5-10)","[10-15)","[15-20)","[20-25)","[25-31)"))

p13CI.all=dplyr::filter(pop1,Site==paste(site))%>%group_by(AgeGroup,YEAR)%>%dplyr::count(pred.serotype)%>%spread(pred.serotype,n)
setnames(p13CI.all, old="Neg", new="Negative")

# Assign NA as 0:

for (idx in 3:8){
  idx.na <- which(is.na(p13CI.all[[idx]]))
  p13CI.all[[idx]][idx.na] <- 0
}

p13CI.all<- tidyr::gather(p13CI.all,"Serostatus","n",3:8)# gather 3 variables (Neg,Prim,Secondary) into 1 variables called "IS"

p13CI.all<- p13CI.all[order(p13CI.all$YEAR,p13CI.all$AgeGroup),]# sort data by year

p13CI.all<- dplyr::mutate(p13CI.all,est=0,lwr.ci=0,upr.ci=0)# create cols for importing result from multinomCI.

for ( i in seq(1,length(p13CI.all$AgeGroup),by=6)){# every 6 rows ,do....
  p13CI.all[i:(i+5), 5:7]<- MultinomCI(c(p13CI.all$n[i:(i+5)]))}



# plot
for (idx.year in ( 1 : length(list_year))){
    p13CI <- dplyr::filter(p13CI.all,YEAR==list_year[idx.year])
    print(ggplot(p13CI, aes(x=AgeGroup,y=est, fill=Serostatus,color=Serostatus))+         geom_point()+
    ggtitle(paste("Proportions",site,dataInput,p13CI$YEAR[1]))+
    theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5))+
    geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25, position=position_dodge(0.2)))

}

```

## fitting data
### Seperated plots

```{r estimated prop and actual prop in one plot,echo=FALSE,fig.height=8,fig.width=12 }
# # actual proportion
# p<- p13CI.all
# p<- p[order(p$Serostatus),]
# 
# # #create function for substr assigning age group as one value, this create the same age structure with p1 data frame below. This function has run in previous chunk => no need re-run in this chunk!
# #
# # my_substr <- function(s){
# #   if (nchar(s) == 5){
# #     t <- substr(s, 4, 4)
# #   }else{
# #     if (nchar(s) == 6){
# #       t <- substr(s, 4, 5)
# #     }else{
# #       t <- substr(s, 5, 6)
# #     }
# #   }
# #   return(t)
# # }
# 
# #
# p$AgeGroup<- apply(p[,1],1,my_substr)
# p <- p[,-4] # exclude column named "n"
# p$ AgeGroup <- as.numeric(p$AgeGroup)
# 
# #*estimated proportion
# p1 <- pest.all[,c("AgeGroup","YEAR","Serostatus","mean","X2.5.","X97.5.")]
# 
# colnames(p1)<- c("AgeGroup","YEAR","Serostatus","est","lwr.ci","upr.ci")
# 
# pc.all<- rbind(data.frame(p), data.frame(p1))# combine estimated and actual data in one 
# 
# 
# #plot negatives
# for ( idx.year in (1:length(list_year))){
# 
#   pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
# 
#   print(
#     ggplot(pc%>%filter(Serostatus=="Neg_est"|Serostatus=="Negative"),
#            aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
#       geom_point()+
#       xlim (1,31)+
#       ylim (0,1)+
#       ggtitle(paste("Neg_serotype specific",site,dataInput,pc$YEAR[1]))+
#       theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
#             axis.text = element_text(face = "bold"))+
#       geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit
#   )
# }
# 
# #plot primary
# for ( idx.year in (1:length(list_year))){
# 
#   pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
# 
#   print(
#     ggplot(pc%>%filter(Serostatus=="Prim1_est"|Serostatus=="1"),
#            aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
#       geom_point()+
#       xlim (1,31)+
#       ylim (0,1)+
#       ggtitle(paste("Prim_serotype specific",site,dataInput,pc$YEAR[1]))+
#       theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
#             axis.text = element_text(face = "bold"))+
#       geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit
#   )
# }
# 
# #plot secondary
# for ( idx.year in (1:length(list_year))){
# 
#   pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
# 
#   print(
#     ggplot(pc%>%filter(Serostatus=="Second_est"|Serostatus=="Secondary"),
#            aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
#       geom_point()+
#       xlim (1,31)+
#       ylim (0,1)+
#       ggtitle(paste("Sec_serotype specific",site,dataInput,pc$YEAR[1]))+
#       theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
#             axis.text = element_text(face = "bold"))+
#       geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit
#   )
# }
# 

```

### All yrs in one plot

```{r estimated prop vs actual prop_ all years in one plot,echo=FALSE,fig.height=8,fig.width=12 }
# actual proportion
p<- p13CI.all
p<- p[order(p$Serostatus),]

# #create function for substr assigning age group as one value, this create the same age structure with p1 data frame below. This function has run in previous chunk => no need re-run in this chunk!
#
# my_substr <- function(s){
#   if (nchar(s) == 5){
#     t <- substr(s, 4, 4)
#   }else{
#     if (nchar(s) == 6){
#       t <- substr(s, 4, 5)
#     }else{
#       t <- substr(s, 5, 6)
#     }
#   }
#   return(t)
# }

#
p$AgeGroup<- apply(p[,1],1,my_substr)
p <- p[,-4] # exclude col named " n"

# estimated proportion
p1 <- pest.all[,c("AgeGroup","YEAR","Serostatus","mean","X2.5.","X97.5.")]

colnames(p1)<- c("AgeGroup","YEAR","Serostatus","est","lwr.ci","upr.ci")

pc.all<- rbind(data.frame(p), data.frame(p1))


pc.all$AgeGroup <- as.numeric(pc.all$AgeGroup)

# # function to get legend from one of the plots => for nicer looking of muliplot => runned in chunk 12
# get_legend<-function(myggplot){
#     tmp <- ggplot_gtable(ggplot_build(myggplot))
#     leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
#     legend <- tmp$grobs[[leg]]
#     return(legend)
#     }

#plot negatives

neg <- list() # create empty list for input graphs in for loop
for ( idx.year in (1:length(list_year))){
    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])

    neg[[idx.year]] <- ggplot(pc%>%filter(Serostatus=="Neg_est"|Serostatus=="Negative"),
                              aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+

        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit

}

legend <- get_legend(neg[[5]])

library(grid)
library(gridExtra)
negplot <- grid.arrange(neg[[1]]+theme(legend.position = "none"),
             neg[[2]]+theme(legend.position = "none"),
             neg[[3]]+theme(legend.position = "none"),
             neg[[4]]+theme(legend.position = "none"),
             neg[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV negatives in",site, "_serotype specific",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page
# # save the figure
# ggsave(filename =paste("Data fit_DENV neg in",site, "_serotype specific",dataInput,".png"),plot=negplot )
ggsave(filename =paste("~/Desktop/PMA analysis results/FoI/serotype specific/fits/Data fit_DENV neg in",site, "_serotype specific",dataInput,".png"),plot=negplot )


#plot primary
## Serotype1
prim1 <- list()
for ( idx.year in (1:length(list_year))){

    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])

    prim1[[idx.year]]<- ggplot(pc%>%filter(Serostatus=="Prim1_est"|Serostatus=="1"),
                              aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+

        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit

}

legend <- get_legend(prim1[[5]])
primplot1 <- grid.arrange(prim1[[1]]+theme(legend.position = "none"),
             prim1[[2]]+theme(legend.position = "none"),
             prim1[[3]]+theme(legend.position = "none"),
             prim1[[4]]+theme(legend.position = "none"),
             prim1[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV1 in",site, "FoI_serotype specific",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page
# # save the figure
# ggsave(filename =paste("Data fit_DENV1 in",site, "_serotype specific",dataInput,".png"),plot=primplot1 )
ggsave(filename =paste("~/Desktop/PMA analysis results/FoI/serotype specific/fits/Data fit_DENV1 in",site, "_serotype specific",dataInput,".png"),plot=primplot1 )

## Serotype2
prim2 <- list()
for ( idx.year in (1:length(list_year))){

    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])

    prim2[[idx.year]]<- ggplot(pc%>%filter(Serostatus=="Prim2_est"|Serostatus=="2"),
                              aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+

        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit

}

legend <- get_legend(prim2[[5]])
primplot2 <- grid.arrange(prim2[[1]]+theme(legend.position = "none"),
             prim2[[2]]+theme(legend.position = "none"),
             prim2[[3]]+theme(legend.position = "none"),
             prim2[[4]]+theme(legend.position = "none"),
             prim2[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV2 in",site, "FoI_serotype specific",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page
# # save the figure
# ggsave(filename =paste("Data fit_DENV2 in",site, "FoI_serotype specific",dataInput,".png"),plot=primplot2 )
ggsave(filename =paste("~/Desktop/PMA analysis results/FoI/serotype specific/fits/Data fit_DENV2 in",site, "FoI_serotype specific",dataInput,".png"),plot=primplot2 )
## Serotype3
prim3 <- list()
for ( idx.year in (1:length(list_year))){

    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])

    prim3[[idx.year]]<- ggplot(pc%>%filter(Serostatus=="Prim3_est"|Serostatus=="3"),
                              aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
        geom_point()+
        xlim (1,31)+
        ylim (0,0.5)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+

        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit

}

legend <- get_legend(prim3[[5]])
primplot3 <- grid.arrange(prim3[[1]]+theme(legend.position = "none"),
             prim3[[2]]+theme(legend.position = "none"),
             prim3[[3]]+theme(legend.position = "none"),
             prim3[[4]]+theme(legend.position = "none"),
             prim3[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV3 in",site, "FoI_serotype specific",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page
# # save the figure
# ggsave(filename =paste("Data fit_DENV3 in",site, "FoI_serotype specific",dataInput,".png"),plot=primplot3 )
ggsave(filename =paste("~/Desktop/PMA analysis results/FoI/serotype specific/fits/Data fit_DENV3 in",site, "FoI_serotype specific",dataInput,".png"),plot=primplot3 )

## Serotype4
prim4 <- list()
for ( idx.year in (1:length(list_year))){

    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])

    prim4[[idx.year]]<- ggplot(pc%>%filter(Serostatus=="Prim4_est"|Serostatus=="4"),
                              aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+

        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit

}

legend <- get_legend(prim4[[5]])
primplot4 <- grid.arrange(prim4[[1]]+theme(legend.position = "none"),
             prim4[[2]]+theme(legend.position = "none"),
             prim4[[3]]+theme(legend.position = "none"),
             prim4[[4]]+theme(legend.position = "none"),
             prim4[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV2 in",site, "FoI_serotype specific",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page
# # save the figure
# ggsave(filename =paste("Data fit_DENV4 in",site, "FoI_serotype specific",dataInput,".png"),plot=primplot4 )
ggsave(filename =paste("~/Desktop/PMA analysis results/FoI/serotype specific/fits/Data fit_DENV4 in",site, "FoI_serotype specific",dataInput,".png"),plot=primplot4 )

#plot secondary
sec <- list()
for ( idx.year in (1:length(list_year))){

    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])


    sec[[idx.year]] <- ggplot(pc%>%filter(Serostatus=="Second_est"|Serostatus=="Secondary"),
                              aes(x=AgeGroup,y=est, fill=Serostatus, color=Serostatus))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+

        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit

}

legend <- get_legend(sec[[5]])
secplot<- grid.arrange(sec[[1]]+theme(legend.position = "none"),
             sec[[2]]+theme(legend.position = "none"),
             sec[[3]]+theme(legend.position = "none"),
             sec[[4]]+theme(legend.position = "none"),
             sec[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV secondary in",site, "_serotype specific",dataInput),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page
# # save the figure
# ggsave(filename =paste("Data fit_DENV secondary in",site, "_serotype specific",dataInput,".png",dataInput,".png"),plot=secplot )
ggsave(filename =paste("~/Desktop/PMA analysis results/FoI/serotype specific/fits/Data fit_DENV secondary in",site, "_serotype specific",dataInput,".png"),plot=secplot )

```


```{r reload saved image into R}
# # library(png)
# # 
# # img = readPNG("/home/phuonght/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Serotype specific/FoI_ serotype specific HC C1D1 .png")
# # grid::grid.raster(img)
# # 
# # 
# # 
# # 
# # Combining all plots in one
# library(gridExtra)
# library(grid)
# # lamb<- grid.arrange(p1,p2,p3,p4,nrow=2,ncol=2)
# lamb <- grid.arrange(p1,p2,p3,p4,nrow=2,ncol=2,bottom=textGrob("Posterior lambda distribution_serotype specific",gp=gpar(fontsize=20,font=8,col="dark blue")))
# 
# 
# 
# # ggsave(filename ="Posterior lambda distribution_serotype specific.png",plot=lamb )

```
