---
title: "FOI_time varying"
author: "Phuong Huynh Thi"
date: "02/05/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

#Initial set up

```{r set wd, echo=FALSE, message=FALSE}
rm(list=ls())
library(dplyr)
library(tidyr)

# Changeable: site:KH or HC?, step year 1, 2 or 5
site <- "KH"
dataInput <-"C1D1" # 6 cases: C1D1, C2D1, C3D1, C1F1, C2F1, C3F1
step_year <- 1 # 1 to 5

setwd("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Time varying")

##Results from different IS and infecting serotype infering models:
if ( dataInput == "C1D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C1D1.csv")  
}
if ( dataInput == "C2D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C2D1.csv")  
}
if ( dataInput == "C3D1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_C3D1.csv")  
}
if ( dataInput == "C1F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C1F1.csv")  
}
if ( dataInput == "C2F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C2F1.csv")  
}
if ( dataInput == "C3F1"){
    data <- read.csv("~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/Infecting serotype Model/PredictedIS_B23_567_pred.serotype_HomoAssigned_C3F1.csv")  
}


data$YEAR <- as.factor(data$YEAR)
data$predictedIS<- ordered(data$predictedIS,levels=c("Secondary","Primary","Neg"))
data$pred.serotype<- as.factor(data$pred.serotype)

pop<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]#cross out acute and ELISA samples
pop$Site <- substr(pop$sampleID,1,2)

#Agegroup_ 1year
pop$AgeGroup <- factor(as.factor(floor(pop$Age)),labels=c("[1-2)","[2-3)","[3-4)","[4-5)","[5-6)","[6-7)","[7-8)","[8-9)","[9-10)","[10-11)","[11-12)","[12-13)","[13-14)","[14-15)","[15-16)","[16-17)","[17-18)","[18-19)","[19-20)","[20-21)","[21-22)","[22-23)","[23-24)","[24-25)","[25-26)","[26-27)","[27-28)","[28-29)","[29-30)","[30,31)"))# group as  1year 1 group.

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
## Agegroup_ 2 years : 16groups

# pop$AgeGroup <-factor(as.factor(floor(pop$Age/2)+1),labels=c("[1-2)","[2-4)","[4-6)","[6-8)","[8-10)","[10-12)","[12-14)","[14-16)","[16-18)","[18-20)","[20-22)","[22-24)","[24-26)","[26-28)","[28-30)","[30-31)"))

#>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
##Agegroup_3years : 11 groups

# pop$AgeGroup <- floor(pop$Age/3) + 1
# pop$AgeGroup[which(pop$AgeGroup == 11)] <- 10
# pop$AgeGroup <- factor(
#   pop$AgeGroup,
#   labels = c("[1-3)","[3-6)","[6-9)","[9-12)","[12-15)","[15-18)",
#              "[18-21)","[21-24)","[24-27)","[27-31)"))
#              
```

# Data input

```{r data input, echo=FALSE, message=FALSE}

# spread(x,y): spread rows of col x into collums, then value of col y will fit in as rows.
#rename(new_name=old_name).

if (site=="HC"){
   p_year=dplyr::filter(pop,Site=="HC")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(predictedIS)%>%spread(predictedIS,n)}
if(site == "KH"){
    p_year=dplyr::filter(pop,Site=="KH")%>%group_by(AgeGroup,YEAR,Site)%>%dplyr::count(predictedIS)%>%spread(predictedIS,n)}

# p_year$total <- apply(p_year[,3:8],1,sum,na.rm=T)

p_year$total <- apply(p_year[,4:6],1,sum,na.rm=T)
p_year <- p_year[order(p_year$YEAR),]

#create function for substr age rather than put age in order, this is useful in case of missing data in a specific age: 
my_substr <- function(s){
  if (nchar(s) == 5){#[2-3)
    t <- substr(s, 4, 4)
  }else{
    if (nchar(s) == 6){ #[9-10)]
      t <- substr(s, 4, 5)
    }else{ #[10-11)]
      t <- substr(s, 5, 6)
    }
  }
  return(t)
}

#
p_year$age<- apply(p_year[,"AgeGroup"],1,my_substr)

# Assign NA as 0 because stan does not support NA value:

for (idx in 4:6){
  idx.na <- which(is.na(p_year[[idx]]))
  p_year[[idx]][idx.na] <- 0
}



# setnames(p_year, old=c("AgeGroup","1","2","3","4","Neg","Secondary","total"),new=c("AgeGroup","DV1.13","DV2.13","DV3.13","DV4.13","Neg.13","Sec.13","total.13"))


```

## Stan formart
This gets the data in the right format for stan.

```{r data format for stan, echo=FALSE,message=FALSE}

b = length(p_year$age)
n_y = 2017-2013+1+max(as.integer(p_year[which(p_year$YEAR==2013),]$age)) # number of years backward, time period that data is available ## KH: 36 -> 1982, HC: 35 -> 1983

if ( step_year == 2){
    if ( site == "KH"){
        vecj = as.integer(c(rep(1:floor(n_y/2), each =  2))) # for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/2), each =  2),17)) # for HC 
    }
} else if (step_year == 3){
    if ( site == "KH"){
        vecj = as.integer(c(rep(1:floor(n_y/3), each =  3))) #for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/3), each =  3),11,11)) # for HC
    }
}else if (step_year == 4){
    if ( site == "KH"){
        vecj = as.integer(c(rep(1:floor(n_y/4), each =  4))) #for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/4), each =  4),9,9,9)) # for HC 
    }
}else if (step_year == 5){
    if ( site == "KH"){
        vecj = as.integer(c(rep(1:floor(n_y/5), each =  5),7)) #for KH
    } else{
        vecj = as.integer(c(rep(1:floor(n_y/5), each =  5))) # for HC 
    }
}else { # step_year = 1
    vecj = as.integer(1:n_y)
}


lamb_y = length(unique(vecj)) # number of lambda over time


# b = length(p_year$age)
# datapp<- list(a = b,
#               datap=c(p_year[1:b,6],
#                       p_year[1:b,5],
#                       p_year[1:b,4]),
#               vecj = vecj,
#               lamb_y = lamb_y,
#               vecy = as.integer(as.character(p_year$YEAR)),
#               veca = as.integer(p_year$age),
#               n_y = n_y) # numbers of neg, prim,and sec respectively. 
# 
# # numbers of neg,prim1,prim2,prim3,prim4,and sec respectively. 
# 
# library(rstan)

b = length(p_year$age)

# number of years: HC: 34 yrs, KH: 35 yrs
n_y <- 2017-2013+max(as.integer(p_year[which(p_year$YEAR==2013),]$age))

l_vecj = length(c(rep(1:round(n_y/step_year), each =  step_year)))

datapp<- list(a = b,
              step_year = step_year,
              datap=c(p_year[1:b,6],
                      p_year[1:b,5],
                      p_year[1:b,4]),
              vecj=as.integer(c(rep(1:round(n_y/step_year), each =  step_year))),#for index of actual lambda
              l_vecj = length(c(rep(1:round(n_y/step_year), each =  step_year))),# length of vecj for later use
              vecy=as.integer(as.character(p_year$YEAR)),
              veca=as.integer(p_year$age)) # numbers of neg, prim,and sec respectively. 

library(rstan)
# index year: 
#2013: 1:23 / 23
#2014: 24:49 / 26
#2015: 50:76 / 27
#2016: 77:101 / 25
#2017: 102:125 / 24

# stan code has sections in it: functions, data (where you tell it what form the data will be in),
#parameters where you say what parameters you are estimating,
#Transformed parameters where you transform these parameters to use in the model
#and the model where you specify how the data and model outcomes are linked
FOI_Dengue <-"~/Dropbox/1.SHARED_FOLDER/slides_June_2018/PMA_batch2To7_July2019/pop data/models/FOI/Time varying/FOI_time varying_step_year.stan"


```

## Simulation
Stan does not support NA in data? => Assign NA as 0

**Some explanation**

Rhat: < 1.05: model perform well
n-eff ratio = n-eff/(0.5 * iter * chains) <1
Iterations: 1/2 Warmup : noise data=> exclude?!, 1/2 Sampling

Posterior distribution (likelihood function= model  and prior distribution: e.g: lamda[0,1] ).

```{r result from model, echo=FALSE, include=FALSE,message=FALSE}
# you then run using this: From this output we can quickly assess model convergence by looking at the Rhat values for each parameter. When these are at or near 1, the chains have converged. There are many other diagnostics, but this is an important one for Stan.

fit<-stan(file = FOI_Dengue,
          data=datapp, iter=6000,
          chains=4,
          cores = parallel::detectCores()) # this may be conducted via 2 steps:  stand_model() and sampling().

# # save data for later use without running code again
# saveRDS(fit,paste("~/Desktop/PMA analysis results/FoI/Time varying/rds/FOI_time varying",step_year,"yr(s)",p_year$Site[1],dataInput,".rds"))

#extract parameters so we can use them as below
posterior<-rstan::extract(fit) # specify package rstan rather tham tidyr
#this summarizes the parameters, gets mean,etc. of parameters and metrics of whether converged or not like Rhat and neff
foisummary<-summary(fit)
# print(foisummary)

```

# Visualisation of results
## Posterior lambda

```{r posterior distribution of lambda, echo=FALSE,fig.height=8,fig.width=12}
#plot the posterior distribution of lambda

#create dataframe for violin plot:
p <- data.frame(lambda = as.numeric(),
                YEAR = as.character()) 

for(a in 1:(l_vecj/step_year)){
  p_temp <- data.frame(lambda = posterior$lambda[ ,a],
                       YEAR = paste0(2018-(step_year*(a-1)+1)))
  p <- rbind(p, p_temp)
}
# 
# # label for KH
# p$YEAR <- factor(p$YEAR,labels = c ("2017-2016","2015-2014","2013-2012","2011-2010","2009-2008","2007-2006","2005-2004","2003-2002","2001-2000","1999-1998","1997-1996","1995-1994","1993-1992","1991-1990","1989-1988","1987-1986","1985-1984","1983"))

# # label for HC
# p$YEAR <- factor(p$YEAR,labels = c ("2017-2016","2015-2014","2013-2012","2011-2010","2009-2008","2007-2006","2005-2004","2003-2002","2001-2000","1999-1998","1997-1996","1995-1994","1993-1992","1991-1990","1989-1988","1987-1986","1985-1984"))

# violin plot
ggplot(p, aes(x=YEAR,y=lambda)) + geom_violin()+
  ggtitle(paste("posterior lambda",step_year,"yr(s)",p_year$Site[1]))+
  theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
        axis.title.x = element_blank(),
        axis.text = element_text(face = "bold", angle = 90, hjust = 1))+
  # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
  # geom_boxplot(width=0.1)+# add median and quartile
  stat_summary(fun.data=mean_sdl, 
               geom="pointrange", color="red")#Add mean and standard deviation


```
## cut last 4 yrs
This is for annually change only.
Look like the last 4 years ( 1986-1984) is noise data. I intend to remove them from the graph 

```{r posterior distribution of lambda- cut last 4 years, echo=FALSE,fig.height=8,fig.width=12}
#plot the posterior distribution of lambda
if(step_year = 1){
  #create dataframe for violin plot:
p <- data.frame(lambda = as.numeric(),
                YEAR = as.character())
rmy <- n_y - 4 # get rid of 4 yrs from the graph

for(a in 1:rmy){
  p_temp <- data.frame(lambda = posterior$lambda[ ,a ],
                       YEAR = paste0(2018-a))
  p <- rbind(p, p_temp)
}

# violin plot
ggplot(p, aes(x=YEAR,y=lambda)) + geom_violin()+
    ggtitle(paste("posterior lambda",step_year,"yr(s)",p_year$Site[1]))+
    ylim(-0.012,0.3)+
    theme(plot.title = element_text(hjust=0.5,face="bold",size=20,colour = "blue"),
          axis.title.x = element_blank(),
          axis.text = element_text(face = "bold", angle = 90, hjust = 1))+
    # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
    # geom_boxplot(width=0.1)+# add median and quartile
    stat_summary(fun.data=mean_sdl, 
                 geom="pointrange", color="red")#Add mean and standard deviation
  
}


```

## seroprevalence by age
The graphs below is for general looking at the data we current have.This is a combination data from 2013 to 2017 by shifting the age to 2017. In other words, if an individual is 2 years old in 2013, the age will be assigned as 6 years old in 2017. By doing this, we assume that all data is collected in 2017 and sample size for each age group is increased. This may lead to under estimating of positives because negatives are keep constant rather than become seroconversion over years.        

```{r seroprevalane accumulation 2017,}

my_substr <- function(s){# AgeGroup
  s <- as.character(s)
  if (nchar(s) == 5){#[2-3]
    t <- substr(s, 4, 4)
  }else{
    if (nchar(s) == 6){#[9-10]
      t <- substr(s, 4, 5)
    }else{#[11-12]
      t <- substr(s, 5, 6)
    }
  }
  return(t)
}

pop_2017<- pop
pop_2017$age <- sapply(pop_2017[,"AgeGroup"],my_substr)
pop_2017$age.17 <- NA

pop_2017$YEAR <- as.numeric(as.character(pop_2017$YEAR))
pop_2017$age <- as.numeric(as.character(pop_2017$age))

for ( i in 1: length(pop_2017$AgeGroup)){
  
  pop_2017$age.17[i] <- pop_2017$age[i] + (2017- pop_2017$YEAR[i])
}




# plot
library(dplyr)
library(grDevices)
# d.17=dplyr::filter(pop_2017,Site=="KH")%>%group_by(age.17,Site,cutoff_5) %>% dplyr::count(age.17)

d.17=dplyr::group_by(pop_2017,age.17,Site,cutoff_5) %>% dplyr::count(age.17)


# Plot in KH
ggplot(d.17%>% filter(Site=="KH"),aes(x=age.17,y=n,fill=cutoff_5))+
  geom_bar(position="fill",stat="identity")+
  # scale_fill_manual(values = c("blue","chocolate3","burlywood3","cornsilk4","azure3","light blue"))+
  # scale_fill_brewer(palette="Spectral")+
  ggtitle("DENV seroprevalence in KH _ 2013-2017")+
  # facet_grid(~YEAR)+
  labs(y="Proportion")+
  scale_x_continuous( breaks = seq(1:35), limits = c (1,36))+
  theme(plot.title =element_text(hjust = 0.5,size=20,face="bold"),
        title=element_text(size=15),
        strip.text.x = element_text(size=18),
        axis.text.x = element_text(angle = 90, size=12,face = "bold"),
        axis.text.y=element_text(size=15, face="bold"),
        axis.title.x = element_blank())


# Plot in HC

ggplot(d.17%>% filter(Site=="HC"),aes(x=age.17,y=n,fill=cutoff_5))+
  geom_bar(position="fill",stat="identity")+
  # scale_fill_manual(values = c("blue","chocolate3","burlywood3","cornsilk4","azure3","light blue"))+
  # scale_fill_brewer(palette="Spectral")+
  ggtitle("DENV seroprevalence in HC _ 2013-2017")+
  # facet_grid(~YEAR)+
  labs(y="Proportion")+
  scale_x_continuous(breaks = seq(1:35), limits = c (1,36))+
  theme(plot.title =element_text(hjust = 0.5,size=20,face="bold"),
        title=element_text(size=15),
        strip.text.x = element_text(size=18),
        axis.text.x = element_text(angle = 90, size=12,face = "bold"),
        axis.text.y=element_text(size=15, face="bold"),
        axis.title.x = element_blank())


```

## Negative

```{r  posterior distribution of neg proportion,echo=FALSE, message=FALSE,fig.height=8,fig.width=12, warning=FALSE}

p_all_year <- data.frame(neg = as.numeric(),
                         age = as.character(),
                         year= as.character())


for(a in 1:b){
  p_temp <- data.frame(neg = posterior$pneg[ , a],
                       age = paste0(p_year$age[a]),
                       year= paste0(p_year$YEAR[a]))
  p_all_year <- rbind(p_all_year, p_temp)
}

# relable factor level of age in order
p_all_year$age <- as.numeric(as.character(p_all_year$age))
p_all_year <- p_all_year[order(p_all_year$age),]
p_all_year$age <- as.factor(p_all_year$age)

library(gridExtra)
library(grid)


list_year <- unique(p_all_year$year)
for (idx.year in 1 : length(list_year)){
  p <- dplyr::filter(p_all_year,year==list_year[idx.year]) # extract data for each year
  
  # length of data frame
  x_max <- length(p$age)
  
  # violin plot
  list.plot <- list()
  
  for (i in 1 : 6){# seperate 6 graphs for each year
    list.plot[[i]] <- ggplot(p[(5*(i-1)*12000 + 1) : min((5*i*12000), x_max),], aes(x=age,y=neg)) +
      geom_violin()+
      theme(plot.subtitle = element_text(hjust=0.5),
            axis.title = element_blank(),
            axis.text = element_text(face = "bold"))+
      # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
      # geom_boxplot(width=0.1)+# add median and quartile
      stat_summary(fun.data=mean_sdl,
                   geom="pointrange", color="red")+#Add mean and sta
      coord_cartesian(ylim=c(0, 1))
  }
  
  (paste("posterior lambda",step_year,"yr(s)",p_year$Site[1]))
  
  grid.arrange(list.plot[[1]],list.plot[[2]],list.plot[[3]],list.plot[[4]],list.plot[[5]], list.plot[[6]], ncol=3,nrow=2, top =textGrob(paste("Negetive_ FoI",step_year,"yr(s)",p_year$Site[1],p$year[1],dataInput),gp=gpar(fontsize=25,col = "blue")))
  
}


```

## Primary

```{r  posterior distribution of primary proportion,echo=FALSE, message=FALSE,fig.height=8,fig.width=12, warning=FALSE}

p_all_year <- data.frame(prim = as.numeric(),
                         age = as.character(),
                         year= as.character())


for(a in 1:b){
  p_temp <- data.frame(prim = posterior$pprimsero[ , a],
                       age = paste0(p_year$age[a]),
                       year= paste0(p_year$YEAR[a]))
  p_all_year <- rbind(p_all_year, p_temp)
}

# relable factor level of age in order
p_all_year$age <- as.numeric(as.character(p_all_year$age))
p_all_year <- p_all_year[order(p_all_year$age),]
p_all_year$age <- as.factor(p_all_year$age)

library(gridExtra)
library(grid)


list_year <- unique(p_all_year$year)
for (idx.year in 1 : length(list_year)){
  p <- dplyr::filter(p_all_year,year==list_year[idx.year]) # extract data for each year
  
  # length of data frame
  x_max <- length(p$age)
  
  # violin plot
  list.plot <- list()
  
  for (i in 1 : 6){# seperate 6 graphs for each year
    list.plot[[i]] <- ggplot(p[(5*(i-1)*12000 + 1) : min((5*i*12000), x_max),], aes(x=age,y=prim)) +
      geom_violin()+
      theme(plot.subtitle = element_text(hjust=0.5),
            axis.title = element_blank(),
            axis.text = element_text(face = "bold"))+
      # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
      # geom_boxplot(width=0.1)+# add median and quartile
      stat_summary(fun.data=mean_sdl,
                   geom="pointrange", color="red")+#Add mean and sta
      coord_cartesian(ylim=c(0, 1))
  }
  
  
  
  grid.arrange(list.plot[[1]],list.plot[[2]],list.plot[[3]],list.plot[[4]],list.plot[[5]], list.plot[[6]], ncol=3,nrow=2, top =textGrob(paste("Primary_FoI",step_year,"yr(s)",p_year$Site[1],p$year[1],dataInput),gp=gpar(fontsize=25,col = "blue")))
  
}


```

##Secondary

```{r  posterior distribution of secondary proportion,echo=FALSE, message=FALSE,fig.height=8,fig.width=12, warning=FALSE}

p_all_year <- data.frame(sec = as.numeric(),
                         age = as.character(),
                         year= as.character())


for(a in 1:b){
  p_temp <- data.frame(sec = posterior$psec[ , a],
                       age = paste0(p_year$age[a]),
                       year= paste0(p_year$YEAR[a]))
  p_all_year <- rbind(p_all_year, p_temp)
}

# relable factor level of age in order
p_all_year$age <- as.numeric(as.character(p_all_year$age))
p_all_year <- p_all_year[order(p_all_year$age),]
p_all_year$age <- as.factor(p_all_year$age)

library(gridExtra)
library(grid)


list_year <- unique(p_all_year$year)
for (idx.year in 1 : length(list_year)){
  p <- dplyr::filter(p_all_year,year==list_year[idx.year]) # extract data for each year
  
  # length of data frame
  x_max <- length(p$age)
  
  # violin plot
  list.plot <- list()
  
  for (i in 1 : 6){# seperate 6 graphs for each year
    list.plot[[i]] <- ggplot(p[(5*(i-1)*12000 + 1) : min((5*i*12000), x_max),],   aes(x=age,y=sec)) +
      geom_violin()+
      theme(plot.subtitle = element_text(hjust=0.5),
            axis.title = element_blank(),
            axis.text = element_text(face = "bold"))+
      # stat_summary(fun.y=mean, geom="point", size=2, color="red")+ # add mean
      # geom_boxplot(width=0.1)+# add median and quartile
      stat_summary(fun.data=mean_sdl,
                   geom="pointrange", color="red")+#Add mean and sta
      coord_cartesian(ylim=c(0, 1))
  }
  
  
  
  grid.arrange(list.plot[[1]],list.plot[[2]],list.plot[[3]],list.plot[[4]],list.plot[[5]], list.plot[[6]], ncol=3,nrow=2, top =textGrob(paste("Secondary_FoI",step_year,"yr(s)",p_year$Site[1],p$year[1],dataInput),gp=gpar(fontsize=25,col = "blue")))
  
}


```

## Pop data
```{r estimated proportion, echo=FALSE, message=FALSE,fig.height=8,fig.width=12}

pest.all<-data.frame(foisummary$summary)
l_pest.all = length(pest.all$mean) # last row og pest.all
d = (l_pest.all - round(n_y/step_year)-1)/3 # 3 group: neg,prim,sec

pest.all<- pest.all[-c(1:round(n_y/step_year),l_pest.all),] # n_y: number of lamda
pest.all$IS <- rep(c("Neg_est","Prim_est","Sec_est"),c(d,d,d))
pest.all$AgeGroup<- as.integer(rep(p_year$age,3))
pest.all$YEAR<- as.integer(rep(as.character(p_year$YEAR),3))
# pest.all$year<- as.factor(pest.all$year)

list_year<- unique(pest.all$YEAR)

for (idx.year in (1 : length(list_year)) ){
  
  pest <- dplyr::filter(pest.all,YEAR==list_year[idx.year])
  
  # print(
  #   ggplot(pest,aes(x=AgeGroup,y=mean, fill=IS,color=IS)) +
  #     geom_point() +
  #     ggtitle(paste("Primary proportion_FOI_changed every year",p_year$Site[1],pest$year[1]))+
  #     theme(plot.title = element_text(color="darkblue",
  #                                     size=20, face="bold",
  #                                     hjust = 0.5),
  #           axis.text = element_text(face = "bold"))+
  #     geom_errorbar(aes(ymin = X2.5., ymax = X97.5.), width = .25)
  # ) 
  
  # grid line by ggplot
  print(ggplot(pest,aes(x=AgeGroup,y=mean, fill=IS,color=IS))+ geom_line()+
          geom_ribbon(aes(ymin=X2.5., ymax = X97.5.),alpha=0.2)+
          ggtitle(paste("Primary_FOI_",step_year,"yr()",p_year$Site[1],pest$YEAR[1],dataInput))+
          xlim(1,31)+
          ylim(0,1)+
          # scale_x_continuous(limits = c(1,31))+
          # scale_y_continuous((limits = c(0,1)))+
          theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
                axis.text = element_text(face = "bold")))
  
}


# # plot grid line:
# 
# library(devtools)
# install_github("lamhm/RUtil")
# library(RUtil)
# # pdf("plot.pdf",width=10,height = 8)# export pdf file
# 
# for (idx.year in (1 : length(list_year)) ){
#   
# pest <- dplyr::filter(pest.all,year==list_year[idx.year])
# 
# subData <- pest[which(pest$IS == "Neg_est") ,]
# plotRanges(x = subData$AgeGroup, yCenter = subData$mean,
#            yLow = subData$X2.5., yHigh = subData$X97.5.,
#            type = "area", centerColour = "blue",
#            rangeColour = colourSetTransparency("blue", alpha = 0.3), ylim = c(0, 1),
#            main=paste("DENV Proportion_FOI_changed every year",p_year$Site[1],pest$year[1]),
#            cex.main=2, col.main = "blue")
# text(2.6,0.7,"Neg",col="blue")
# 
# 
# subData <- pest[which(pest$IS == "Prim_est") ,]
# plotRanges(x = subData$AgeGroup, yCenter = subData$mean,
#            yLow = subData$X2.5., yHigh = subData$X97.5.,
#            type = "area", centerColour = "green",
#            rangeColour = colourSetTransparency("green", alpha = 0.3), newPlot = F)
# text(2.6,0.1,"Prim",col="green")
# 
# subData <- pest[which(pest$IS == "Sec_est") ,]
# plotRanges(x = subData$AgeGroup, yCenter = subData$mean,
#            yLow = subData$X2.5., yHigh = subData$X97.5.,
#            type = "area", centerColour = "red",
#            rangeColour = colourSetTransparency("red", alpha = 0.3), newPlot = F)
# text(5,0,"Sec",col="red")
# 
# }
# 
# # dev.off()

```

# Modelfitting

Regarding actual data, the number of samples in each age group is quite small, I gathered samples in groups of 5 years old rather than those of 1. Therefore, there are 6 groups in total: **[1-5), [5-10),[10-15), [15-20), [20-25), [25-30)**

## Pop data
```{r actual proportion_5yrs group,echo=FALSE, message=FALSE,fig.height=8,fig.width=12}
# CI95%
library(DescTools)
library(data.table)

pop1<- data[which(!is.na(data$AGE_MIN)&is.na(data$PanbioUnit)),]# cross out acute and ELISA samples
pop1$Site <- substr(pop1$sampleID,1,2)

##Agegroup_5years : 6 groups

pop1$AgeGroup <- floor(pop1$Age/5) + 1
pop1$AgeGroup[which(pop1$AgeGroup == 7)]<- 6
pop1$AgeGroup <- factor(
  pop1$AgeGroup,
  labels = c("[1-5)","[5-10)","[10-15)","[15-20)","[20-25)","[25-30)"))


p13CI.all=dplyr::filter(pop1,Site==paste(p_year$Site[1]))%>%group_by(AgeGroup,YEAR)%>%dplyr::count(predictedIS)%>%spread(predictedIS,n)
setnames(p13CI.all, old="Neg", new="Negative")

# Assign NA as 0:

for (idx in 3:5){
  idx.na <- which(is.na(p13CI.all[[idx]]))
  p13CI.all[[idx]][idx.na] <- 0
}

p13CI.all<- tidyr::gather(p13CI.all,"IS","n",3:5)# gather 3 variables (Neg,Prim,Secondary) into 1 variables called "IS"

p13CI.all<- p13CI.all[order(p13CI.all$YEAR,p13CI.all$AgeGroup),]# sort data by year

p13CI.all<- dplyr::mutate(p13CI.all,est=0,lwr.ci=0,upr.ci=0)# create cols for importing result from multinomCI, NA!

for ( i in seq(1,length(p13CI.all$AgeGroup),by=3)){# every 3 rows ,do....
  p13CI.all[i:(i+2), 5:7]<- MultinomCI(c(p13CI.all$n[i:(i+2)]))}



# # plot
# for (idx.year in ( 1 : length(list_year))){
#   p13CI <- dplyr::filter(p13CI.all,YEAR==list_year[idx.year])
#   print(ggplot(p13CI, aes(x=AgeGroup,y=est, fill=IS,color=IS))+ geom_point()+
#           ggtitle(paste("Proportions",p_year$Site[1],p13CI$YEAR[1]))+
#           theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5))+
#           geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25, position=position_dodge(0.2)))
# 
# }

```

## Seperated plots
```{r estimated prop and actual prop in one plot,echo=FALSE,fig.height=8,fig.width=12 }
# actual proportion
p<- p13CI.all
p<- p[order(p$IS),]

# #create function for substr assigning age group as one value, this create the same age structure with p1 data frame below. This function has run in previous chunk => no need re-run in this chunk!
# 
# my_substr <- function(s){
#   if (nchar(s) == 5){
#     t <- substr(s, 4, 4)
#   }else{
#     if (nchar(s) == 6){
#       t <- substr(s, 4, 5)
#     }else{
#       t <- substr(s, 5, 6)
#     }
#   }
#   return(t)
# }

#
p$AgeGroup<- apply(p[,1],1,my_substr)
p <- p[,-4]

# estimated proportion
p1 <- pest.all[,c("AgeGroup","YEAR","IS","mean","X2.5.","X97.5.")]

colnames(p1)<- c("AgeGroup","YEAR","IS","est","lwr.ci","upr.ci")

pc.all<- rbind(data.frame(p), data.frame(p1))


pc.all$AgeGroup <- as.numeric(pc.all$AgeGroup)

#plot negatives
for ( idx.year in (1:length(list_year))){
  
  pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
  
  print(
    ggplot(pc%>%filter(IS=="Neg_est"|IS=="Negative"),
           aes(x=AgeGroup,y=est, fill=IS, color=IS))+
      geom_point()+
      xlim (1,31)+
      ylim (0,1)+
      ggtitle(paste("Neg_FOI_",step_year,"yr(s)",p_year$Site[1],pc$YEAR[1],dataInput))+
      theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
            axis.text = element_text(face = "bold"))+
      geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit 
  )
}

#plot primary
for ( idx.year in (1:length(list_year))){
  
  pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
  
  print(
    ggplot(pc%>%filter(IS=="Prim_est"|IS=="Primary"),
           aes(x=AgeGroup,y=est, fill=IS, color=IS))+
      geom_point()+
      xlim (1,31)+
      ylim (0,1)+
      ggtitle(paste("Prim_FOI_",step_year,"yr(s)",p_year$Site[1],pc$YEAR[1],dataInput))+
      theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
            axis.text = element_text(face = "bold"))+
      geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit 
  )
}

#plot secondary
for ( idx.year in (1:length(list_year))){
  
  pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
  
  print(
    ggplot(pc%>%filter(IS=="Second_est"|IS=="Secondary"),
           aes(x=AgeGroup,y=est, fill=IS, color=IS))+
      geom_point()+
      xlim (1,31)+
      ylim (0,1)+
      ggtitle(paste("Sec_FOI_",step_year,"yr(s)",p_year$Site[1],pc$YEAR[1],dataInput))+
      theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
            axis.text = element_text(face = "bold"))+
      geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position = position_dodge(0.5))# move CI to the left or the right a bit 
  )
}

```

## 

```{r estimated prop and actual prop_ all years in one plot,echo=FALSE,fig.height=8,fig.width=12 }
# actual proportion
p<- p13CI.all
p<- p[order(p$IS),]

p$AgeGroup<- apply(p[,"AgeGroup"],1,my_substr)
p <- p[,-4]

# estimated proportion
p1 <- pest.all[,c("AgeGroup","YEAR","IS","mean","X2.5.","X97.5.")]

colnames(p1)<- c("AgeGroup","YEAR","IS","est","lwr.ci","upr.ci")

pc.all<- rbind(data.frame(p), data.frame(p1))


pc.all$AgeGroup <- as.numeric(pc.all$AgeGroup)

# # function to get legend from one of the plots => for nicer looking of muliplot => runned in chunk 12
# get_legend<-function(myggplot){
#     tmp <- ggplot_gtable(ggplot_build(myggplot))
#     leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
#     legend <- tmp$grobs[[leg]]
#     return(legend)
#     }

#plot negatives

neg <- list() # create empty list for input graphs in for loop
for ( idx.year in (1:length(list_year))){
    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
    
    neg[[idx.year]] <- ggplot(pc%>%filter(IS=="Neg_est"|IS=="Negative"),
                              aes(x=AgeGroup,y=est, fill=IS, color=IS))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+
        
        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit 
    
}

legend <- get_legend(neg[[5]])

library(grid)
library(gridExtra)
grid.arrange(neg[[1]]+theme(legend.position = "none"),
             neg[[2]]+theme(legend.position = "none"),
             neg[[3]]+theme(legend.position = "none"),
             neg[[4]]+theme(legend.position = "none"),
             neg[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV negatives in",p_year$Site, "_FoI",step_year,"yr(s)"),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page 


#plot primary
prim <- list()
for ( idx.year in (1:length(list_year))){
    
    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
    
    prim[[idx.year]]<- ggplot(pc%>%filter(IS=="Prim_est"|IS=="Primary"),
                              aes(x=AgeGroup,y=est, fill=IS, color=IS))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+
        
        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit 
    
}

legend <- get_legend(prim[[5]])
grid.arrange(prim[[1]]+theme(legend.position = "none"),
             prim[[2]]+theme(legend.position = "none"),
             prim[[3]]+theme(legend.position = "none"),
             prim[[4]]+theme(legend.position = "none"),
             prim[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV primary infection in",p_year$Site, "_FoI",step_year,"yr(s)"),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page 


#plot secondary
sec <- list()
for ( idx.year in (1:length(list_year))){
    
    pc <- dplyr::filter(pc.all,YEAR==list_year[idx.year])
    
    
    sec[[idx.year]] <- ggplot(pc%>%filter(IS=="Second_est"|IS=="Secondary"),
                              aes(x=AgeGroup,y=est, fill=IS, color=IS))+
        geom_point()+
        xlim (1,31)+
        ylim (0,1)+
        ggtitle(paste(pc$YEAR[1]))+
        theme(plot.title = element_text(color="darkblue", size=20, face="bold", hjust = 0.5),
              axis.text = element_text(face = "bold"))+
        
        geom_errorbar(aes(ymax = upr.ci, ymin = lwr.ci), width = .25,position =         position_dodge(0.5))# move CI to the left or the right a bit 
    
}

legend <- get_legend(sec[[5]])
grid.arrange(sec[[1]]+theme(legend.position = "none"),
             sec[[2]]+theme(legend.position = "none"),
             sec[[3]]+theme(legend.position = "none"),
             sec[[4]]+theme(legend.position = "none"),
             sec[[5]]+theme(legend.position = "none"),
             legend, nrow=3,ncol=2,
             bottom = textGrob(paste("DENV secondary infection in",p_year$Site, "_FoI",step_year,"yr(s)"),gp=gpar(fontsize=20,fontface="bold"))) # all plot in one page 


```



